---
title: "Literature_Review_Analysis"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(janitor)
library(viridis)
library(GGally)
library(plyr)
library(reshape2)

```

# Read Data

```{r}

papers <- read.delim("lit_review_data.csv", 
                     sep = ",") %>%
  clean_names()

papers

```

```{r}

paper_data <- papers %>% 
  select(c(title, 
           country, 
           continent, 
           response_category, 
           local_strategy, 
           local_effect, 
           landscape_effect, 
           minimum_complexity, 
           maximum_complexity, 
           interaction_effect)) %>%
  mutate_at(c('title',
              'country', 
              'continent',
              'response_category', 
              'local_strategy', 
              'local_effect', 
              'landscape_effect', 
              'minimum_complexity', 
              'maximum_complexity',
              'interaction_effect'), as.factor)
paper_data

```

# Geographical Distribution 

```{r}

papers %>% 
  distinct(title, .keep_all = TRUE) %>%
  select(c(country, 
           continent)) %>%
  ggplot(aes(x = continent)) +
  geom_bar()

```

```{r}

papers %>% 
  distinct(title, .keep_all = TRUE) %>%
  select(c(country, 
           continent)) %>%
  filter(continent == 'Europe') %>%
  ggplot(aes(x = country)) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 45))

```

## Local Diversification Strategy 

Subset main table by local diversification strategy category.

```{r}

floral <- paper_data %>% 
  filter(local_strategy == 'Floral')

diversity <- paper_data %>% 
  filter(local_strategy == 'Diversity')

intensity <- paper_data %>% 
  filter(local_strategy == 'Intensity')

structure <- paper_data %>% 
  filter(local_strategy == 'Structure')

```

Floral counts. 

```{r}

floral_local_positive <- sum(na.omit(floral$local_effect == 'Positive'))
floral_local_negative <- sum(na.omit(floral$local_effect == 'Negative'))
floral_local_ns <- sum(na.omit(floral$local_effect == 'NS'))

floral_landscape_positive <- sum(na.omit(floral$landscape_effect == 'Positive'))
floral_landscape_negative <- sum(na.omit(floral$landscape_effect == 'Negative'))
floral_landscape_ns <- sum(na.omit(floral$landscape_effect == 'NS'))

floral_interaction_sig <- sum(na.omit(floral$interaction_effect != 'NS'))
floral_interaction_ns <- sum(na.omit(floral$interaction_effect == 'NS'))

```

Diversity counts. 

```{r}

diversity_local_positive <- sum(na.omit(diversity$local_effect == 'Positive'))
diversity_local_negative <- sum(na.omit(diversity$local_effect == 'Negative'))
diversity_local_ns <- sum(na.omit(diversity$local_effect == 'NS'))

diversity_landscape_positive <- sum(na.omit(diversity$landscape_effect == 'Positive'))
diversity_landscape_negative <- sum(na.omit(diversity$landscape_effect == 'Negative'))
diversity_landscape_ns <- sum(na.omit(diversity$landscape_effect == 'NS'))

diversity_interaction_sig <- sum(na.omit(diversity$interaction != 'NS'))
diversity_interaction_ns <- sum(na.omit(diversity$interaction == 'NS'))

```

Intensity counts. 

```{r}

intensity_local_positive <- sum(na.omit(intensity$local_effect == 'Positive'))
intensity_local_negative <- sum(na.omit(intensity$local_effect == 'Negative'))
intensity_local_ns <- sum(na.omit(intensity$local_effect == 'NS'))

intensity_landscape_positive <- sum(na.omit(intensity$landscape_effect == 'Positive'))
intensity_landscape_negative <- sum(na.omit(intensity$landscape_effect == 'Negative'))
intensity_landscape_ns <- sum(na.omit(intensity$landscape_effect == 'NS'))

intensity_interaction_sig <- sum(na.omit(intensity$interaction != 'NS'))
intensity_interaction_ns <- sum(na.omit(intensity$interaction == 'NS'))

```

Structure counts. 

```{r}

structure_local_positive <- sum(na.omit(structure$local_effect == 'Positive'))
structure_local_negative <- sum(na.omit(structure$local_effect == 'Negative'))
structure_local_ns <- sum(na.omit(structure$local_effect == 'NS'))

structure_landscape_positive <- sum(na.omit(structure$landscape_effect == 'Positive'))
structure_landscape_negative <- sum(na.omit(structure$landscape_effect == 'Negative'))
structure_landscape_ns <- sum(na.omit(structure$landscape_effect == 'NS'))

structure_interaction_sig <- sum(na.omit(structure$interaction != 'NS'))
structure_interaction_ns <- sum(na.omit(structure$interaction == 'NS'))

```


## Response Category

```{r}

levels(paper_data$response_category)

```

```{r}

arthropod <- paper_data %>% 
  filter(response_category == 'Arthropod')

crop <- paper_data %>% 
  filter(response_category == 'Crop')

natural_enemy <- paper_data %>% 
  filter(response_category == 'Natural enemy')

pest <- paper_data %>% 
  filter(response_category == 'Pest')

pollinator <- paper_data %>% 
  filter(response_category == 'Pollinator')

```

Arthropod responses. 

```{r}

arthropod_local_positive <- sum(na.omit(arthropod$local_effect == 'Positive'))
arthropod_local_negative <- sum(na.omit(arthropod$local_effect == 'Negative'))
arthropod_local_ns <- sum(na.omit(arthropod$local_effect == 'NS'))

arthropod_landscape_positive <- sum(na.omit(arthropod$landscape_effect == 'Positive'))
arthropod_landscape_negative <- sum(na.omit(arthropod$landscape_effect == 'Negative'))
arthropod_landscape_ns <- sum(na.omit(arthropod$landscape_effect == 'NS'))

arthropod_interaction_sig <- sum(na.omit(arthropod$interaction != 'NS'))
arthropod_interaction_ns <- sum(na.omit(arthropod$interaction == 'NS'))

```

Crop responses. 

```{r}

crop_local_positive <- sum(na.omit(crop$local_effect == 'Positive'))
crop_local_negative <- sum(na.omit(crop$local_effect == 'Negative'))
crop__local_ns <- sum(na.omit(crop$local_effect == 'NS'))

crop_landscape_positive <- sum(na.omit(crop$landscape_effect == 'Positive'))
crop_landscape_negative <- sum(na.omit(crop$landscape_effect == 'Negative'))
crop_landscape_ns <- sum(na.omit(crop$landscape_effect == 'NS'))

crop_interaction_sig <- sum(na.omit(crop$interaction != 'NS'))
crop_interaction_ns <- sum(na.omit(crop$interaction == 'NS'))

```

Natural enemy responses. 

```{r}

ne_local_positive <- sum(na.omit(natural_enemy$local_effect == 'Positive'))
ne_local_negative <- sum(na.omit(natural_enemy$local_effect == 'Negative'))
ne_local_ns <- sum(na.omit(natural_enemy$local_effect == 'NS'))

ne_landscape_positive <- sum(na.omit(natural_enemy$landscape_effect == 'Positive'))
ne_landscape_negative <- sum(na.omit(natural_enemy$landscape_effect == 'Negative'))
ne_landscape_ns <- sum(na.omit(natural_enemy$landscape_effect == 'NS'))

ne_interaction_sig <- sum(na.omit(natural_enemy$interaction != 'NS'))
ne_interaction_ns <- sum(na.omit(natural_enemy$interaction == 'NS'))

```

Pest responses. 

```{r}

pest_local_positive <- sum(na.omit(pest$local_effect == 'Positive'))
pest_local_negative <- sum(na.omit(pest$local_effect == 'Negative'))
pest_local_ns <- sum(na.omit(pest$local_effect == 'NS'))

pest_landscape_positive <- sum(na.omit(pest$landscape_effect == 'Positive'))
pest_landscape_negative <- sum(na.omit(pest$landscape_effect == 'Negative'))
pest_landscape_ns <- sum(na.omit(pest$landscape_effect == 'NS'))

pest_interaction_sig <- sum(na.omit(pest$interaction != 'NS'))
pest_interaction_ns <- sum(na.omit(pest$interaction == 'NS'))

```

Pollinator responses. 

```{r}

pollinator_local_positive <- sum(na.omit(pollinator$local_effect == 'Positive'))
pollinator_local_negative <- sum(na.omit(pollinator$local_effect == 'Negative'))
pollinator_local_ns <- sum(na.omit(pollinator$local_effect == 'NS'))

pollinator_landscape_positive <- sum(na.omit(pollinator$landscape_effect == 'Positive'))
pollinator_landscape_negative <- sum(na.omit(pollinator$landscape_effect == 'Negative'))
pollinator_landscape_ns <- sum(na.omit(pollinator$landscape_effect == 'NS'))

pollinator_interaction_sig <- sum(na.omit(pollinator$interaction != 'NS'))
pollinator_interaction_ns <- sum(na.omit(pollinator$interaction == 'NS'))

```

## Landscape Type

```{r}

levels(paper_data$landscape_type)

```

```{r}

non_crop <- paper_data %>% filter(landscape_type == 'Non-crop area')
prop_organic <- paper_data %>% filter(landscape_type == 'Proportion organic')
woody <- paper_data %>% filter(landscape_type == 'Woody habitat')
field_size <- paper_data %>% filter(landscape_type == 'Field size')
non_maize <- paper_data %>% filter(landscape_type == 'Non-maize area')
prop_reduced_intensity <- paper_data %>% filter(landscape_type == 'Proportion reduced intensity')
grassland <- paper_data %>% filter(landscape_type == 'Grassland')
pollinator_habitat <- paper_data %>% filter(landscape_type == 'Pollinator habitat')
semi_natural <- paper_data %>% filter(landscape_type == 'Semi/natural habitat')

```

Non-crop landscape.

```{r}

non_crop_local_positive <- sum(na.omit(non_crop$local_effect == 'Positive'))
non_crop_local_negative <- sum(na.omit(non_crop$local_effect == 'Negative'))
non_crop_local_ns <- sum(na.omit(non_crop$local_effect == 'NS'))

non_crop_landscape_positive <- sum(na.omit(non_crop$landscape_effect == 'Positive'))
non_crop_landscape_negative <- sum(na.omit(non_crop$landscape_effect == 'Negative'))
non_crop_landscape_ns <- sum(na.omit(non_crop$landscape_effect == 'NS'))

non_crop_interaction_sig <- sum(na.omit(non_crop$interaction != 'NS'))
non_crop_interaction_ns <- sum(na.omit(non_crop$interaction == 'NS'))

```

Natural/semi-natural landscape.

```{r}

semi_natural_local_positive <- sum(na.omit(semi_natural$local_effect == 'Positive'))
semi_natural_local_negative <- sum(na.omit(semi_natural$local_effect == 'Negative'))
semi_natural_local_ns <- sum(na.omit(semi_natural$local_effect == 'NS'))

semi_natural_landscape_positive <- sum(na.omit(semi_natural$landscape_effect == 'Positive'))
semi_natural_landscape_negative <- sum(na.omit(semi_natural$landscape_effect == 'Negative'))
semi_natural_landscape_ns <- sum(na.omit(semi_natural$landscape_effect == 'NS'))

semi_natural_interaction_sig <- sum(na.omit(semi_natural$interaction != 'NS'))
semi_natural_interaction_ns <- sum(na.omit(semi_natural$interaction == 'NS'))

```

Proportion organic in landscape.

```{r}

prop_organic_local_positive <- sum(na.omit(prop_organic$local_effect == 'Positive'))
prop_organic_local_negative <- sum(na.omit(prop_organic$local_effect == 'Negative'))
prop_organic_local_ns <- sum(na.omit(prop_organic$local_effect == 'NS'))

prop_organic_landscape_positive <- sum(na.omit(prop_organic$landscape_effect == 'Positive'))
prop_organic_landscape_negative <- sum(na.omit(prop_organic$landscape_effect == 'Negative'))
prop_organic_landscape_ns <- sum(na.omit(prop_organic$landscape_effect == 'NS'))

prop_organic_interaction_sig <- sum(na.omit(prop_organic$interaction != 'NS'))
prop_organic_interaction_ns <- sum(na.omit(prop_organic$interaction == 'NS'))

```

Proportion organic in landscape.

```{r}

woody_local_positive <- sum(na.omit(woody$local_effect == 'Positive'))
woody_local_negative <- sum(na.omit(woody$local_effect == 'Negative'))
woody_local_ns <- sum(na.omit(woody$local_effect == 'NS'))

woody_landscape_positive <- sum(na.omit(woody$landscape_effect == 'Positive'))
woody_landscape_negative <- sum(na.omit(woody$landscape_effect == 'Negative'))
woody_landscape_ns <- sum(na.omit(woody$landscape_effect == 'NS'))

woody_interaction_sig <- sum(na.omit(woody$interaction != 'NS'))
woody_interaction_ns <- sum(na.omit(woody$interaction == 'NS'))

```

Field size.

```{r}

field_size_local_positive <- sum(na.omit(field_size$local_effect == 'Positive'))
field_size_local_negative <- sum(na.omit(field_size$local_effect == 'Negative'))
field_size_local_ns <- sum(na.omit(field_size$local_effect == 'NS'))

field_size_landscape_positive <- sum(na.omit(field_size$landscape_effect == 'Positive'))
field_size_landscape_negative <- sum(na.omit(field_size$landscape_effect == 'Negative'))
field_size_landscape_ns <- sum(na.omit(field_size$landscape_effect == 'NS'))

field_size_interaction_sig <- sum(na.omit(field_size$interaction != 'NS'))
field_size_interaction_ns <- sum(na.omit(field_size$interaction == 'NS'))

```

Non-maize in landscape.

```{r}

non_maize_local_positive <- sum(na.omit(non_maize$local_effect == 'Positive'))
non_maize_size_local_negative <- sum(na.omit(non_maize$local_effect == 'Negative'))
non_maize_size_local_ns <- sum(na.omit(non_maize$local_effect == 'NS'))

non_maize_size_landscape_positive <- sum(na.omit(non_maize$landscape_effect == 'Positive'))
non_maize_size_landscape_negative <- sum(na.omit(non_maize$landscape_effect == 'Negative'))
non_maize_size_landscape_ns <- sum(na.omit(non_maize$landscape_effect == 'NS'))

non_maize_size_interaction_sig <- sum(na.omit(non_maize$interaction != 'NS'))
non_maize_size_interaction_ns <- sum(na.omit(non_maize$interaction == 'NS'))

```

Reduced intensity in landscape.

```{r}

reduced_intensity_local_positive <- sum(na.omit(prop_reduced_intensity$local_effect == 'Positive'))
reduced_intensity_size_local_negative <- sum(na.omit(prop_reduced_intensity$local_effect == 'Negative'))
reduced_intensity_size_local_ns <- sum(na.omit(prop_reduced_intensity$local_effect == 'NS'))

reduced_intensity_size_landscape_positive <- sum(na.omit(prop_reduced_intensity$landscape_effect == 'Positive'))
reduced_intensity_size_landscape_negative <- sum(na.omit(prop_reduced_intensity$landscape_effect == 'Negative'))
reduced_intensity_size_landscape_ns <- sum(na.omit(prop_reduced_intensity$landscape_effect == 'NS'))

reduced_intensity_size_interaction_sig <- sum(na.omit(prop_reduced_intensity$interaction != 'NS'))
reduced_intensity_size_interaction_ns <- sum(na.omit(prop_reduced_intensity$interaction == 'NS'))

```

Grassland in landscape.

```{r}

grassland_local_positive <- sum(na.omit(grassland$local_effect == 'Positive'))
grassland__local_negative <- sum(na.omit(grassland$local_effect == 'Negative'))
grassland_local_ns <- sum(na.omit(grassland$local_effect == 'NS'))

grassland_landscape_positive <- sum(na.omit(grassland$landscape_effect == 'Positive'))
grassland_landscape_negative <- sum(na.omit(grassland$landscape_effect == 'Negative'))
grassland_landscape_ns <- sum(na.omit(grassland$landscape_effect == 'NS'))

grassland_interaction_sig <- sum(na.omit(grassland$interaction != 'NS'))
grassland_interaction_ns <- sum(na.omit(grassland$interaction == 'NS'))

```

Pollinator habitat in landscape.

```{r}

pollinator_habitat_local_positive <- sum(na.omit(pollinator_habitat$local_effect == 'Positive'))
pollinator_habitat_local_negative <- sum(na.omit(pollinator_habitat$local_effect == 'Negative'))
pollinator_habitat_local_ns <- sum(na.omit(pollinator_habitat$local_effect == 'NS'))

pollinator_habitat_landscape_positive <- sum(na.omit(pollinator_habitat$landscape_effect == 'Positive'))
pollinator_habitat_landscape_negative <- sum(na.omit(pollinator_habitat$landscape_effect == 'Negative'))
pollinator_habitat_landscape_ns <- sum(na.omit(pollinator_habitat$landscape_effect == 'NS'))

pollinator_habitat_interaction_sig <- sum(na.omit(pollinator_habitat$interaction != 'NS'))
pollinator_habitat_interaction_ns <- sum(na.omit(pollinator_habitat$interaction == 'NS'))

```

# EDA - Visualizations

Local effects, faceted by local diversification strategy (Floral, Diversity, Intensity, Structure). 

```{r}

local_effects_df <- paper_data %>%
  filter(local_effect == 'Positive' | 
           local_effect == 'Negative' | 
           local_effect == 'NS') 

local_strategy_counts <- ddply(.data = local_effects_df, 
                 .(local_strategy), 
                 summarize, 
                 n = paste("n =", length(local_effect)))

local_effects_df %>%
  mutate(local_effect = factor(local_effect, levels = c('Positive', 
                                                        'Negative', 
                                                        'NS'))) %>%
  ggplot(aes(x = local_effect, 
             fill = local_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local Diversification Strategy Effects') +
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local Diversification Strategy') + 
  ylab('Number of Observations') +
  labs(fill = 'Local Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ local_strategy) +
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = local_strategy_counts, 
            aes(x = 1.8, y = 5, label = n), 
            vjust = -10, hjust = 2,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 215)) +
  scale_fill_viridis(discrete = TRUE)

```

Landscape effects, faceted by local diversification strategy (Floral, Diversity, Intensity, Structure). 

```{r}

landscape_effects_df <- paper_data %>%
  filter(landscape_effect == 'Positive' | 
           landscape_effect == 'Negative' | 
           landscape_effect == 'NS') %>%
  mutate(as.factor(landscape_effect))

landscape_strategy_counts <- ddply(.data = landscape_effects_df, 
                 .(local_strategy), 
                 summarize, 
                 n = paste("n =", length(landscape_effect)))

landscape_effects_df %>%
  mutate(landscape_effect = factor(landscape_effect, 
                                   levels = c('Positive', 
                                              'Negative', 
                                              'NS'))) %>%
  ggplot(aes(x = landscape_effect, 
             fill = landscape_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Landscape Diversification Effects') +
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Landscape Diversification Gradient') + 
  ylab('Number of Observations') +
  labs(fill = 'Landscape Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ local_strategy) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = landscape_strategy_counts, 
            aes(x = 1.8, y = 5, label = n), 
            vjust = -10, 
            hjust = 1.75,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 225)) +
  scale_fill_viridis(discrete = TRUE)

```

Local effects, faceted by response category (Crop, Arthropod, Natural Enemy, Pest, Pollinator, Other). 

```{r}

local_category_counts <- ddply(.data = local_effects_df, 
                 .(response_category), 
                 summarize, 
                 n = paste("n =", length(local_effect)))

local_effects_df %>% 
  mutate(local_effect = factor(local_effect, 
                               levels = c('Positive', 'Negative', 'NS'))) %>%
  ggplot(aes(x = local_effect, 
             fill = local_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local Diversification Strategy Effects on Specific Response Categories') +
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local Diversification Strategy') +  
  ylab('Number of Observations') +
  labs(fill = 'Local Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ response_category) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = local_category_counts, 
            aes(x = 1.8, y = 5, label = n), 
            vjust = -10, 
            hjust = 1.2,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 200)) +
  scale_fill_viridis(discrete = TRUE)

```

Landscape effects, faceted by response category (Crop, Arthropod, Natural Enemy, Pest, Pollinator, Other). 

```{r}

landscape_category_counts <- ddply(.data = landscape_effects_df, 
                 .(response_category), 
                 summarize, 
                 n = paste("n =", length(landscape_effect)))

landscape_effects_df %>%
  mutate(landscape_effect = factor(landscape_effect, 
                                   levels = c('Positive', 
                                              'Negative', 
                                              'NS'))) %>%
  ggplot(aes(x = landscape_effect, fill = landscape_effect, by = 1)) + 
  geom_bar() +
  ggtitle('Landscape Diversification Effects') +
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Landscape Diversification Gradient') + 
  ylab('Number of Observations') +
  labs(fill = 'Landscape Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ response_category) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = landscape_category_counts, 
            aes(x=1.8, y=5, label = n), 
            vjust = -10, 
            hjust = 1.25,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 200)) +
  scale_fill_viridis(discrete = TRUE)

```

```{r}

interaction_df <- paper_data %>%
  filter(interaction_effect == 'NS' | interaction_effect != 'NS') %>%
  mutate(interaction_effect = case_when(
    interaction_effect == 'NS' ~ 'NS',
    interaction_effect != 'NS' ~ 'S'
    )) %>% 
  mutate(as.factor(interaction_effect)) 

interaction_category_counts <- ddply(.data = interaction_df, 
                 .(response_category), 
                 summarize, 
                 n = paste("n =", length(interaction_effect)))

interaction_strategy_counts <- ddply(.data = interaction_df, 
                 .(local_strategy), 
                 summarize, 
                 n = paste("n =", length(interaction_effect)))

interaction_df %>%
  mutate(interaction_effect = factor(interaction_effect, 
                                     levels = c('S', 'NS'))) %>%
  ggplot(aes(x = interaction_effect, 
             fill = interaction_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local and Landscape Interaction Effects') + 
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local and Landscape Interaction') + 
  ylab('Number of Observations') +
  labs(fill = 'Interaction Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ response_category) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = interaction_category_counts, 
            aes(x = 1.8, y = 5, label = n), 
            vjust = -11, 
            hjust = 1.75,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 300)) +
  scale_fill_viridis(discrete = TRUE) 


interaction_df %>%
  mutate(interaction_effect = factor(interaction_effect, 
                                     levels = c('S', 'NS'))) %>%
  ggplot(aes(x = interaction_effect, 
             fill = interaction_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local and Landscape Interaction Effects') + 
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local and Landscape Interaction') + 
  ylab('Number of Observations') +
  labs(fill = 'Interaction Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45)) +
  facet_wrap(~ local_strategy) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = interaction_strategy_counts, 
            aes(x = 0.5, y = 5, label = n), 
            vjust = -11, 
            hjust = -0.1,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 325)) +
  scale_fill_viridis(discrete = TRUE) 

```

Segment local and landscape interaction into more granular responses. 

- More positive in simple landscapes x
- More negative in simple landscapes x
- More positive in intermediate landscapes x
- More negative in intermediate landscapes x
- More positive in complex landscapes x
- More negative in complex landscapes x

- Less positive in simple landscapes 
- Less negative in simple landscapes
- Less positive in intermediate landscapes 
- Less negative in intermediate landscapes 
- Less positive in complex landscapes 
- Less negative in complex landscapes 

```{r, fig.width = 12, fig.height. =4}

paper_data %>%
  filter(interaction_effect != 'NS') %>%
  mutate(interaction_effect = recode(interaction_effect, 
                           "Less negative local effect in complex landscapes" = "Less Neg - Complex",
                           "Less negative local effect in intermediate landscapes" = "Less Neg - Intermediate",
                           "Less positive local effect in complex landscapes" = "Less Pos - Complex",
                           "Less positive local effect in intermediate landscapes" = "Less Pos - Intermediate",
                           "More negative local effect in complex landscapes" = "More Neg - Complex",
                           "More negative local effect in intermediate landscapes" = "More Neg - Intermediate",
                           "More negative local effect in simple landscapes" = "More Neg - Simple",
                           "More positive local effect in complex landscapes" = "More Pos - Complex",
                           "More positive local effect in intermediate landscapes" = "More Pos - Intermediate",
                           "More positive local effect in simple landscapes" = "More Pos - Simple")) %>%
  ggplot(aes(x = interaction_effect, 
             fill = interaction_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local and Landscape Interaction Effects') + 
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local and Landscape Interaction') + 
  ylab('Number of Observations') +
  labs(fill = 'Interaction Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45), 
                   label = abbreviate) +
  facet_wrap(~ response_category) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = interaction_category_counts, 
            aes(x = 1.8, y = 5, label = n), 
            vjust = -11, 
            hjust = 1,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 20)) +
  scale_fill_viridis(discrete = TRUE)

```

```{r, fig.width=12, fig.height=4}

paper_data %>%
  filter(interaction_effect != 'NS') %>%
  mutate(interaction_effect = recode(interaction_effect, 
                           "Less negative local effect in complex landscapes" = "Less Neg - Complex",
                           "Less negative local effect in intermediate landscapes" = "Less Neg - Intermediate",
                           "Less positive local effect in complex landscapes" = "Less Pos - Complex",
                           "Less positive local effect in intermediate landscapes" = "Less Pos - Intermediate",
                           "More negative local effect in complex landscapes" = "More Neg - Complex",
                           "More negative local effect in intermediate landscapes" = "More Neg - Intermediate",
                           "More negative local effect in simple landscapes" = "More Neg - Simple",
                           "More positive local effect in complex landscapes" = "More Pos - Complex",
                           "More positive local effect in intermediate landscapes" = "More Pos - Intermediate",
                           "More positive local effect in simple landscapes" = "More Pos - Simple")) %>%
  ggplot(aes(x = interaction_effect, 
             fill = interaction_effect, 
             by = 1)) + 
  geom_bar() +
  ggtitle('Local and Landscape Interaction Effects') + 
  theme(plot.title = element_text(hjust = .5)) +
  xlab('Effect of Local and Landscape Interaction') + 
  ylab('Number of Observations') +
  labs(fill = 'Interaction Effect') +
  scale_x_discrete(guide = guide_axis(angle = 45), 
                   label = abbreviate) +
  facet_wrap(~ local_strategy) + 
  geom_text(aes(label = scales::percent(after_stat(prop), accuracy = 1)), 
            stat = "prop", 
            position = position_dodge(width = 0.9), 
            vjust = -0.5) +
  geom_text(data = interaction_strategy_counts, 
            aes(x=1.8, y=5, label = n), 
            vjust = -11, 
            hjust = 1.5,
            colour = "black", 
            inherit.aes = FALSE, 
            parse = FALSE) +
  expand_limits(y = c(0, 15)) +
  scale_fill_viridis(discrete = TRUE)


```

## Plotting Landscape Ranges 

```{r}

papers %>% distinct(title, .keep_all = TRUE) %>%
  filter(interaction_effect == 'NS') %>%
  arrange(desc(minimum_complexity)) %>%
  mutate(paper_num = c(1:length(title))) %>%
  select(paper_num, 
         minimum_complexity, 
         maximum_complexity) %>%
  melt(id.vars = 'paper_num') %>%
  mutate_at('value', as.factor) %>%
  ggplot(aes(x = value, 
             y = paper_num)) + 
  geom_line(aes(group = paper_num)) 

```

```{r, fig.width = 6, fig.height = 10}

papers %>%
  arrange(desc(minimum_complexity)) %>%
  mutate(paper_num = c(1:583)) %>%
  select(paper_num, 
         minimum_complexity,
         maximum_complexity) %>%
  melt(id.vars = 'paper_num') %>%
  mutate_at('value', as.factor) %>%
  ggplot(aes(x = value, 
             y = paper_num)) + 
  geom_line(aes(group = paper_num)) 


```











