---
title: "Organic_Farming_Survey_EDA"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
```


Data upload - Eli's Organic Farming Survey results.

```{r}

organic_farming <- read.delim("Bloom_SurveyDataExtension.csv", sep = ",", na.strings = c("", "NA"))
organic_farming

```

Select columns describing the types of crops grown by respondents, plot bar graph to see frequency of each crop.

```{r}

organic_farming %>%
  select(Participant.ID, B6_Brassica:B6_Ericaceae) %>%
  stack(B6_Brassica:B6_Ericaceae) %>%
  na.omit() %>%
  ggplot(aes(x = fct_infreq(values))) +
  geom_bar() +
  scale_x_discrete(guide = guide_axis(angle = 45))

```

Of the options, the most frequently grown crop categories are Brassica, Allium, Curcubit, and Solanaceous. Determine what potential pest and natural enemy systems exist in each one + other pros and cons of working in each system.

BRASSICA
Go to farmers and see if I can do experiment. 

ALLIUM


CUCURBIT


SOLANACEOUS

