---
title: "Silvopastoral_Survey"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(janitor)

```

Replace "si" or "no" answers with corresponding score value.

- Regeneration = 1 h1_1_3  
- Planting trees = 2 h1_1_4 
- Live fences = 2 h1_1_5
- Silvopastoral = 3 h1_1_6
- Forage banks = 3 h1_1_7

- No = 0 for all of the questions

# Read Data

This is an initial subset of the survey data and only includes the answers to Module H, which asks about specific silvopastoral practices being implemented on the farm. 

```{r}

module_h <- read.delim("Data/module_h_responses.csv", sep = ",")

module_h <- module_h %>% 
  clean_names()

head(module_h)

```

# Generate Score

Create column for proportion of land cover by the practice for each of the relevant questions. 

```{r}

module_h <- module_h %>% 
  mutate(h1_1_3_prop = h1_3_3 / area_of_the_farm, .after = h1_3_3) %>% 
  mutate(h1_1_4_prop = h1_3_4 / area_of_the_farm, .after = h1_3_4) %>%
  mutate(h1_1_5_prop = h1_3_5 / area_of_the_farm, .after = h1_3_5) %>%
  mutate(h1_1_6_prop = h1_3_6 / area_of_the_farm, .after = h1_3_6) %>%
  mutate(h1_1_7_prop = h1_3_7 / area_of_the_farm, .after = h1_3_7)
  
```


  
  

Multiply score by proportion. 

Sum together individual question scores into a cummulative score for the farm's silvopastoral intensity.




