---
title: "Silvopastoral_Survey"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(janitor)

```

Replace "si" or "no" answers with corresponding score value.

- Regeneration = 1 h1_1_3  
- Planting trees = 2 h1_1_4 
- Live fences = 2 h1_1_5
- Silvopastoral = 3 h1_1_6
- Forage banks = 3 h1_1_7

- No = 0 for all of the questions

# Read Data

This is an initial subset of the survey data and only includes the answers to Module H, which asks about specific silvopastoral practices being implemented on the farm. 

```{r}

module_h <- read.delim("Data/module_h_responses.csv", sep = ",")

module_h <- module_h %>% 
  clean_names() %>%
  replace(is.na(.), 0)

head(module_h)

```

# Generate Score

Create column for proportion of land cover by the practice for each of the relevant questions. 

```{r}

module_h <- module_h %>% 
  mutate(h1_1_3_prop = h1_3_3 / area_of_the_farm, .after = h1_3_3) %>% 
  mutate(h1_1_4_prop = h1_3_4 / area_of_the_farm, .after = h1_3_4) %>%
  mutate(h1_1_5_prop = h1_3_5 / area_of_the_farm, .after = h1_3_5) %>%
  mutate(h1_1_6_prop = h1_3_6 / area_of_the_farm, .after = h1_3_6) %>%
  mutate(h1_1_7_prop = h1_3_7 / area_of_the_farm, .after = h1_3_7)
  
```

Modify "si" and "no" answers into equivalent numerical scores. 

```{r}

# Practices worth 1 point. 

module_h <- module_h %>% 
  mutate(h1_1_3_score = case_when(h1_1_3 == 'Si' ~ 1,
  h1_1_3 == 'No' ~ 0), .after = h1_1_3)
  
# Practices worth 2 points. 

module_h <- module_h %>% 
  mutate(h1_1_4_score = case_when(h1_1_4 == 'Si' ~ 2,
  h1_1_4 == 'No' ~ 0), .after = h1_1_4)

module_h <- module_h %>% 
  mutate(h1_1_5_score = case_when(h1_1_5 == 'Si' ~ 2,
  h1_1_5 == 'No' ~ 0), .after = h1_1_5)

# Practices worth 3 points. 

module_h <- module_h %>% 
  mutate(h1_1_6_score = case_when(h1_1_6 == 'Si' ~ 3,
  h1_1_6 == 'No' ~ 0), .after = h1_1_6)

module_h <- module_h %>% 
  mutate(h1_1_7_score = case_when(h1_1_7 == 'Si' ~ 3,
  h1_1_7 == 'No' ~ 0), .after = h1_1_7)

```

Generate cumulative score by summing value of each question weighted by proportion of land cover under that practice. 

```{r}

module_h <- module_h %>% 
  mutate(score = h1_1_3_score * h1_1_3_prop +
           h1_1_4_score * h1_1_4_prop +
           h1_1_5_score * h1_1_5_prop +
           h1_1_6_score * h1_1_6_prop +
           h1_1_7_score * h1_1_7_prop) %>%
  mutate(score = replace(score, score < 0, NA))

```

Check distribution of scores. Average score = 0.7675455

```{r}

mean_score = mean(na.omit(module_h$score))
mean_score

module_h %>% ggplot(aes(x = score)) +
  geom_histogram(bins = 50) + 
  geom_vline(aes(xintercept = mean_score), color = "red", linewidth = 1) + 
  ggtitle('Distribution of Scores')

```
















