---
title: "Corn_Pest_CDL_Processing"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(janitor)

```

# Read Data

Data upload for CDL landscape data + CDL metadata for NY - 2002, 2012, 2022. 

```{r}

CDL_Metadata_NY_2022 <- read.delim('CDL_Metadata_NY_2022.csv', sep = ",")
CDL_Metadata_NY_2012 <- read.delim('CDL_Metadata_NY_2012.csv', sep = ",")
CDL_Metadata_NY_2002 <- read.delim('CDL_Metadata_NY_2002.csv', sep = ",")

Corn_Pest_CDL_NY_2km_2022 <- read.delim('Raw_CDL_Data/corn_pest_ny_2km_2022.csv', sep = ",")
Corn_Pest_CDL_NY_5km_2022 <- read.delim('Raw_CDL_Data/corn_pest_ny_5km_2022.csv', sep = ",")

Corn_Pest_CDL_NY_2km_2012 <- read.delim('Raw_CDL_Data/corn_pest_ny_2km_2012.csv', sep = ",")
Corn_Pest_CDL_NY_5km_2012 <- read.delim('Raw_CDL_Data/corn_pest_ny_5km_2012.csv', sep = ",")

Corn_Pest_CDL_NY_2km_2002 <- read.delim('Raw_CDL_Data/corn_pest_ny_2km_2002.csv', sep = ",")
Corn_Pest_CDL_NY_5km_2002 <- read.delim('Raw_CDL_Data/corn_pest_ny_5km_2002.csv', sep = ",")

```

Formatting the metadata so that it can be merged with the QGIS output files--the CDL number needs to have "VALUE" written in front of it so that it can match.

```{r}

CDL_Metadata_NY_2022 <- CDL_Metadata_NY_2022 %>% 
  mutate(cdl_code = paste("VALUE", cdl_number, sep = "_"))

CDL_Metadata_NY_2012 <- CDL_Metadata_NY_2012 %>% 
  mutate(cdl_code = paste("VALUE", cdl_number, sep = "_"))

CDL_Metadata_NY_2002 <- CDL_Metadata_NY_2002 %>% 
  mutate(cdl_code = paste("VALUE", cdl_number, sep = "_"))

```

Merging QGIS outputs with the metadata so that the crops are displayed by name not value.

```{r}

CDL_Crops_NY_2km_2022 <- Corn_Pest_CDL_NY_2km_2022 %>% 
  select(Name, VALUE_0:VALUE_244) %>% 
  setNames(CDL_Metadata_NY_2022$cdl_classification[match(names(.), CDL_Metadata_NY_2022$cdl_code)]) %>% 
  clean_names()

CDL_Crops_NY_5km_2022 <- Corn_Pest_CDL_NY_5km_2022 %>% 
  select(Name, VALUE_0:VALUE_244) %>% 
  setNames(CDL_Metadata_NY_2022$cdl_classification[match(names(.), CDL_Metadata_NY_2022$cdl_code)]) %>% 
  clean_names()

CDL_Crops_NY_2km_2012 <- Corn_Pest_CDL_NY_2km_2012 %>% 
  select(Name, VALUE_0:VALUE_243) %>% 
  setNames(CDL_Metadata_NY_2012$cdl_classification[match(names(.), CDL_Metadata_NY_2012$cdl_code)]) %>% 
  clean_names()

CDL_Crops_NY_5km_2012 <- Corn_Pest_CDL_NY_5km_2012 %>% 
  select(Name, VALUE_0:VALUE_243) %>% 
  setNames(CDL_Metadata_NY_2012$cdl_classification[match(names(.), CDL_Metadata_NY_2012$cdl_code)]) %>% 
  clean_names()

CDL_Crops_NY_2km_2002 <- Corn_Pest_CDL_NY_2km_2002 %>% 
  select(Name, VALUE_0:VALUE_176) %>% 
  setNames(CDL_Metadata_NY_2002$cdl_classification[match(names(.), CDL_Metadata_NY_2002$cdl_code)]) %>% 
  clean_names()

CDL_Crops_NY_5km_2002 <- Corn_Pest_CDL_NY_5km_2002 %>% 
  select(Name, VALUE_0:VALUE_176) %>% 
  setNames(CDL_Metadata_NY_2002$cdl_classification[match(names(.), CDL_Metadata_NY_2002$cdl_code)]) %>% 
  clean_names()

```

Grouping corn and sweet corn as a total. 

```{r}

CDL_Crops_NY_2km_2022 <- CDL_Crops_NY_2km_2022 %>% 
  mutate(total_corn = corn + sweet_corn, .before = na_2) %>%
  rename(site = na)

CDL_Crops_NY_5km_2022 <- CDL_Crops_NY_5km_2022 %>% 
  mutate(total_corn = corn + sweet_corn, .before = na_2) %>%
  rename(site = na)

CDL_Crops_NY_2km_2012 <- CDL_Crops_NY_2km_2012 %>% 
  mutate(total_corn = corn + sweet_corn, .before = na_2) %>%
  rename(site = na)

CDL_Crops_NY_5km_2012 <- CDL_Crops_NY_5km_2012 %>% 
  mutate(total_corn = corn + sweet_corn, .before = na_2) %>%
  rename(site = na)

CDL_Crops_NY_2km_2002 <- CDL_Crops_NY_2km_2002 %>% 
  mutate(total_corn = corn, .before = na_2) %>%
  rename(site = na)

CDL_Crops_NY_5km_2002 <- CDL_Crops_NY_5km_2002 %>% 
  mutate(total_corn = corn, .before = na_2) %>%
  rename(site = na)

```

Calculating total land. 

```{r}

CDL_Crops_NY_2km_2022 <- CDL_Crops_NY_2km_2022 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_2km_2022, na_2:cauliflower)))

CDL_Crops_NY_5km_2022 <- CDL_Crops_NY_5km_2022 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_5km_2022, na_2:cauliflower)))
  
CDL_Crops_NY_2km_2012 <- CDL_Crops_NY_2km_2012 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_2km_2012, na_2:cabbage)))
  
CDL_Crops_NY_5km_2012 <- CDL_Crops_NY_5km_2012 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_5km_2022, na_2:cabbage)))
  
CDL_Crops_NY_2km_2002 <- CDL_Crops_NY_2km_2002 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_2km_2002, na_2:na_9)))
  
CDL_Crops_NY_5km_2002 <- CDL_Crops_NY_5km_2002 %>% 
  mutate(total_land = rowSums(select(CDL_Crops_NY_5km_2002, na_2:na_9)))
  
```

Calculating proportion of corn within total land. 

```{r}

CDL_Crops_NY_2km_2022 <- CDL_Crops_NY_2km_2022 %>% 
  mutate(prop_corn = total_corn / total_land)

CDL_Crops_NY_5km_2022 <- CDL_Crops_NY_5km_2022 %>% 
  mutate(prop_corn = total_corn / total_land)
  
CDL_Crops_NY_2km_2012 <- CDL_Crops_NY_2km_2012 %>% 
  mutate(prop_corn = total_corn / total_land)
  
CDL_Crops_NY_5km_2012 <- CDL_Crops_NY_5km_2012 %>% 
  mutate(prop_corn = total_corn / total_land)
  
CDL_Crops_NY_2km_2002 <- CDL_Crops_NY_2km_2002 %>% 
  mutate(prop_corn = total_corn / total_land)
  
CDL_Crops_NY_5km_2002 <- CDL_Crops_NY_5km_2002 %>% 
  mutate(prop_corn = total_corn / total_land)
  
```

```{r}

Corn_NY_2km_2022 <- CDL_Crops_NY_2km_2022 %>% 
  select(c(site, total_corn, corn, sweet_corn, prop_corn, total_land))

# write.csv(Corn_NY_2km_2022, file = "final_cdl_corn_2km_2022.csv")

Corn_NY_5km_2022 <- CDL_Crops_NY_5km_2022 %>% 
  select(c(site, total_corn, corn, sweet_corn, prop_corn, total_land))

# write.csv(Corn_NY_5km_2022, file = "final_cdl_corn_5km_2022.csv")

Corn_NY_2km_2012 <- CDL_Crops_NY_2km_2012 %>% 
  select(c(site, total_corn, corn, sweet_corn, prop_corn, total_land))

# write.csv(Corn_NY_2km_2012, file = "final_cdl_corn_2km_2012.csv")

Corn_NY_5km_2012 <- CDL_Crops_NY_5km_2012 %>% 
  select(c(site, total_corn, corn, sweet_corn, prop_corn, total_land))

# write.csv(Corn_NY_5km_2012, file = "final_cdl_corn_5km_2012.csv")
  
```

# EDA - Descriptive Statistics

```{r}

CDL_Crops_NY_2km_2022 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (2km Radius), New York 2022')
  
```

```{r}

summary(CDL_Crops_NY_2km_2022$prop_corn)

```

```{r}

CDL_Crops_NY_5km_2022 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (5km Radius), New York 2022')
  
```

```{r}

summary(CDL_Crops_NY_5km_2022$prop_corn)

```

```{r}

CDL_Crops_NY_2km_2012 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (2km Radius), New York 2012')
  
```

```{r}

summary(CDL_Crops_NY_2km_2012$prop_corn)

```

```{r}

CDL_Crops_NY_5km_2012 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (5km Radius), New York 2012')
  
```

```{r}

summary(CDL_Crops_NY_5km_2012$prop_corn)

```

```{r}

CDL_Crops_NY_2km_2002 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (2km Radius), New York 2002')
  
```

```{r}

summary(CDL_Crops_NY_2km_2002$prop_corn)

```

```{r}

CDL_Crops_NY_5km_2002 %>% 
  ggplot(aes(x = prop_corn)) +
  geom_histogram() +
  ggtitle('Distribution of Proportion of Corn (5km Radius), New York 2002')
  
```

```{r}

summary(CDL_Crops_NY_5km_2002$prop_corn)

```




