---
title: "dung_beetle_soil"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(fitdistrplus)
library(lme4)
library(DHARMa)
library(rsq)
library(effects)
library(marginaleffects)
library(glmmTMB)
library(performance)
library(insight)
library(MuMIn)

```

Read in data frame - soil data downloaded from https://casoilresource.lawr.ucdavis.edu/soil-properties/download.php and raster points extracted using QGIS. 

```{r}

dung_beetle <- read.delim("Data/diversity_landscape.csv", sep = ",")

dung_beetle <- dung_beetle %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
  mutate(farm = as.factor(farm)) %>%
  mutate(season = as.factor(season)) %>%
  mutate(drainage = as.factor(drainage)) %>%
  mutate(soil_texture = as.factor(soil_texture))

head(dung_beetle)

```

Divide data by year. 

```{r}

dung_beetle_22 <- dung_beetle %>% filter(year == '2022')
dung_beetle_24 <- dung_beetle %>% filter(year == '2024')

```

# Total abundance 

All models include day of year, soil texture and drainage class as fixed effects and farm as a random effect. For each response variable, there is a model for each year. 

### 2022

```{r}

# Model total abundance vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model1a <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      soil_texture +
                      drainage)^2 +
                      (1 | farm), 
                    data = dung_beetle_22, 
                    na.action='na.fail')

# Full model - AIC 1469.0
# No significant interactions.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1469.9

model1a <- glmer.nb(total_abundance ~ scale(julian_day) +
                      soil_texture +
                      drainage +
                      (1 | farm), 
                    data = dung_beetle_22, 
                    na.action='na.fail')

summary(model1a)

# check_model(model1a)

```

### 2024

```{r}

# Model total abundance vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model1b <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      soil_texture +
                      drainage)^2 +
                      (1 | farm), 
                    data = dung_beetle_24, 
                    na.action='na.fail')

# Full model - AIC 1332.3
# No significant interactions.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1332.5

model1b <- glmer.nb(total_abundance ~ scale(julian_day) +
                      soil_texture +
                      drainage +
                      (1 | farm), 
                    data = dung_beetle_24, 
                    na.action='na.fail')

summary(model1b)

# check_model(model1a)

```

# Richness

### 2022 

```{r}

# Model richness vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model2a <- glmer(q_0_richness ~ (scale(julian_day) +
                      soil_texture +
                      drainage)^2 +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

# Full model - AIC 722.8
# No significant interactions. Only Julian day is significant.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 715.1

model2a <- glmer(q_0_richness ~ scale(julian_day) + 
                      soil_texture + 
                      drainage +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

summary(model2a)

# check_model(model2)

```

### 2024

```{r}

# Model richness vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model2b <- glmer(q_0_richness ~ (scale(julian_day) +
                      soil_texture +
                      drainage)^2 +
                      (1 | farm), 
                    data = dung_beetle_24, family='poisson',
                    na.action='na.fail')

# Full model - AIC 649.8
# No significant interactions. Only Julian day is significant.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 643.7

model2b <- glmer(q_0_richness ~ scale(julian_day) + 
                      soil_texture + 
                      drainage + 
                      (1 | farm), 
                    data = dung_beetle_24, family='poisson',
                    na.action='na.fail')

summary(model2b)

# check_model(model2)

```

# Shannon

```{r}

# Look at log transformation.

dung_beetle_q1 <- dung_beetle %>% drop_na(q_1_shannon)
dung_beetle_q1$shannon_log <- log(dung_beetle_q1$q_1_shannon)

dung_beetle_q1_22 <- dung_beetle_q1 %>% filter(year == '2022')
dung_beetle_q1_24 <- dung_beetle_q1 %>% filter(year == '2024')

```

### 2022 

```{r}

# Model Shannon index vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3a <- glmmTMB(shannon_log ~ (scale(julian_day) + 
                                   soil_texture + 
                                   drainage)^2 + 
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_22)

# Full model - AIC 225.6
# No significant interactions.

model3a <- glmmTMB(shannon_log ~ scale(julian_day) + 
                                   soil_texture + 
                                   drainage +
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 221.2
  
summary(model3a)

# check_model(model3)

```

### 2024

```{r}

# Model Shannon index vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3b <- glmmTMB(shannon_log ~ (scale(julian_day) + 
                                   soil_texture + 
                                   drainage)^2 + 
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_24)

# Full model - AIC 218.8
# No significant interactions.

model3b <- glmmTMB(shannon_log ~ scale(julian_day) + 
                                   soil_texture + 
                                   drainage +
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_24)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 221.2
  
summary(model3b)

# check_model(model3)

```

# Simpson

```{r}

# Look at log transformation.

dung_beetle_q2 <- dung_beetle %>% drop_na(q_2_simpson)
dung_beetle_q2$simpson_log <- log(dung_beetle_q2$q_2_simpson)

dung_beetle_q2_22 <- dung_beetle_q2 %>% filter(year == '2022')
dung_beetle_q2_24 <- dung_beetle_q2 %>% filter(year == '2024')

```

### 2022

```{r}

# Model Simpson index vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4a <- glmmTMB(simpson_log ~ (scale(julian_day) + 
                                    drainage + 
                                    soil_texture)^2 + 
                     (1 | farm), ziformula=~1, data=dung_beetle_q2_22)

# Full model - AIC 195.8
# No significant interactions.

model4a <- glmmTMB(simpson_log ~ scale(julian_day) + 
                                   drainage + 
                                   soil_texture +
                    (1 | farm), ziformula=~1, data=dung_beetle_q2_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 195.2

summary(model4a)

# check_model(model4)

```

### 2024

```{r}

# Model Simpson index vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4b <- glmmTMB(simpson_log ~ (scale(julian_day) + 
                                    drainage + 
                                    soil_texture)^2 + 
                     (1 | farm), ziformula=~1, data=dung_beetle_q2_24)

# Full model - AIC 190.4
# No significant interactions.

model4b <- glmmTMB(simpson_log ~ scale(julian_day) + 
                                   drainage + 
                                   soil_texture +
                    (1 | farm), ziformula=~1, data=dung_beetle_q2_24)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 191.7

summary(model4b)

# check_model(model4)

```

# Native species abundance

### 2022 

```{r}

# Model native species abundance vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model5a <- glmer.nb(native_species_abundance ~ (scale(julian_day) + 
                                                  soil_texture + 
                                                  drainage)^2 + 
                      (1 | farm), data = dung_beetle_22)

# Full model - AIC 536.8
# Significant interactions - Julian*drainage5, soil_texture5*drainage4, soil_texture5*drainage8

model5a <- glmer.nb(native_species_abundance ~ scale(julian_day) + 
                                   soil_texture + 
                                   drainage + 
                     scale(julian_day)*soil_texture +
                     soil_texture*drainage +
                    (1 | farm), data=dung_beetle_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 539.1

summary(model5a)

# check_model(model5)

```

### 2024

```{r}

# Model native species abundance vs. day of year, soil texture, and drainage class (and all two-way interactions). Farm as random variable. 

model5b <- glmer.nb(native_species_abundance ~ (scale(julian_day) + 
                                                  soil_texture + 
                                                  drainage)^2 + 
                      (1 | farm), data = dung_beetle_24)

# Full model - AIC 695.0
# Significant interactions - soil_texture5*drainage5

model5b <- glmer.nb(native_species_abundance ~ scale(julian_day) + 
                                   soil_texture + 
                                   drainage + 
                     soil_texture*drainage +
                    (1 | farm), data=dung_beetle_24)

# Model keeping the significant interactions of the global model - helped with convergence too.
# Simplified model - AIC 687.9

summary(model5b)

# check_model(model5)

```

# Native species richness

### 2022

```{r}

# Model native species richness vs. day of year, soil texture, drainage class (and all two-way interactions). Farm as random variable. 

model6a <- glmer(native_species_richness ~ (scale(julian_day) + 
                                             soil_texture + 
                                             drainage)^2 + 
                  (1 | farm), data = dung_beetle_22, family = poisson)

# Full model - AIC 382.7
# Significant interactions - soil_texture5*drainage8, soil_texture5*drainage4

model6a <- glmer(native_species_richness ~ scale(julian_day) + 
                                             soil_texture + 
                                             drainage + 
                                             soil_texture*drainage + 
                  (1 | farm), data = dung_beetle_22, family = poisson)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 379.9

summary(model6a)

# check_model(model6)

```

### 2024

```{r}

# Model native species richness vs. day of year, soil texture, drainage class (and all two-way interactions). Farm as random variable. 

model6b <- glmer(native_species_richness ~ (scale(julian_day) + 
                                             soil_texture + 
                                             drainage)^2 + 
                  (1 | farm), data = dung_beetle_24, family = poisson)

# Full model - AIC 408.4
# No significant interactions

model6b <- glmer(native_species_richness ~ scale(julian_day) + 
                                             soil_texture + 
                                             drainage + 
                  (1 | farm), data = dung_beetle_24, family = poisson)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 399.7

summary(model6b)

# check_model(model6)

```

# Native species proportion

### 2022

```{r}

# Model native species proportion vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7a <- glmmTMB(native_species_proportion ~ (scale(julian_day) + 
                                                  drainage + 
                                                  soil_texture)^2 + 
                     (1 | farm), data = dung_beetle_22, family=ordbeta)

# Full model - AIC 190.8
# Significant interactions - Julian day*drainage5, Julian day*soil_texture 5

model7a <- glmmTMB(native_species_proportion ~ scale(julian_day) + 
                                                  drainage + 
                                                  soil_texture + 
                                                  scale(julian_day)*drainage +
                     scale(julian_day)*drainage + 
                     (1 | farm), data = dung_beetle_22, family=ordbeta)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 203.1

summary(model7a)

# check_model(model7)

```

### 2024

```{r}

# Model native species proportion vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7b <- glmmTMB(native_species_proportion ~ (scale(julian_day) + 
                                                  drainage + 
                                                  soil_texture)^2 + 
                     (1 | farm), data = dung_beetle_24, family=ordbeta)

# Full model - AIC 70.3
# No significant interactions

model7b <- glmmTMB(native_species_proportion ~ scale(julian_day) + 
                                                  drainage + 
                                                  soil_texture + 
                     (1 | farm), data = dung_beetle_24, family=ordbeta)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 71.4

summary(model7b)

# check_model(model7)

```

