---
title: "dung_beetle_landscape"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(fitdistrplus)
library(lme4)
library(DHARMa)
library(rsq)
library(effects)
library(marginaleffects)
library(glmmTMB)
library(performance)
library(insight)
library(MuMIn)

```

Read in data frame - landscape data pulled from USDA CDL at 1000m radius around each trapping point. Convert data types. 

All landscape data is pulled from the USDA CDL. Agriculture includes all annual and perennial crops. Woodland includes all forested habitat + shrubland. Semi-natural habitat includes pastures and grasslands. 

```{r}

dung_beetle <- read.delim("Data/diversity_landscape.csv", sep = ",")

dung_beetle <- dung_beetle %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
  mutate(farm = as.factor(farm)) %>%
  mutate(season = as.factor(season))

head(dung_beetle)

```

Divide data by year. 

```{r}

dung_beetle_22 <- dung_beetle %>% filter(year == '2022')
dung_beetle_24 <- dung_beetle %>% filter(year == '2024')

```

# Total abundance 

All models include Julian date, woodland proportion (forests, shrublands), agriculture proportion (all agriculture types), and semi-natural habitat proportion as fixed effects and farm as a random effect. For each response variable, there is a model for each year. 

```{r}

# Check distributions. 
plot(fitdist(dung_beetle_22$total_abundance,"nbinom"))
plot(fitdist(dung_beetle_24$total_abundance,"nbinom"))

```

### 2022

```{r}

# Model total abundance vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model1a <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_22, 
                    na.action='na.fail')

# Full model - AIC 1474.4
# Only Julian day and landscape interactions were significant, no landscape-landscape interactions.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1472.2

model1a <- glmer.nb(total_abundance ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) + 
                      scale(julian_day)*scale(woodland_prop) + 
                      scale(julian_day)*scale(ag_prop) + 
                      scale(julian_day)*scale(semi_nat_prop) + 
                      (1 | farm), 
                    data = dung_beetle_22)

summary(model1a)

# check_model(model1a)

```

### 2024

```{r}

# Model total abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model1b <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_24, 
                    na.action='na.fail')

# Full model - AIC 1317.1
# Significant interactions - Julian day * prop_ag, woodland_prop*ag_prop.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1319.9

model1b <- glmer.nb(total_abundance ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) + 
                      scale(julian_day)*scale(ag_prop) + 
                      scale(woodland_prop)*scale(ag_prop) +
                      (1 | farm), 
                    data = dung_beetle_24)

summary(model1b)

# check_model(model1b)

```

# Richness

```{r}

plot(fitdist(dung_beetle_22$q_0_richness,"pois"))
plot(fitdist(dung_beetle_24$q_0_richness,"pois"))

```

### 2022 

```{r}

# Model richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model2a <- glmer(q_0_richness ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

# Full model - AIC 725.4
# No significant interactions. Only Julian day is significant.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 718.5

model2a <- glmer(q_0_richness ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

summary(model2a)

# check_model(model2)

```

### 2024 

```{r}

# Model richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model2b <- glmer(q_0_richness ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_24, family='poisson',
                    na.action='na.fail')

# Full model - AIC 632.9
# No significant interactions. Only Julian day is significant.

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 630.3

model2b <- glmer(q_0_richness ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) +
                      (1 | farm), 
                    data = dung_beetle_24, family='poisson',
                    na.action='na.fail')

summary(model2b)

# check_model(model2)

```

# Shannon

```{r}

# Look at log transformation.

dung_beetle_q1 <- dung_beetle %>% drop_na(q_1_shannon)
dung_beetle_q1$shannon_log <- log(dung_beetle_q1$q_1_shannon)

dung_beetle_q1_22 <- dung_beetle_q1 %>% filter(year == '2022')
dung_beetle_q1_24 <- dung_beetle_q1 %>% filter(year == '2024')

plot(fitdist(dung_beetle_q1$shannon_log,"norm"))

```

### 2022 

```{r}

# Model Shannon index vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3a <- glmmTMB(shannon_log ~ (scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop))^2 + 
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_22)

# Full model - AIC 219.1
# Significant interactions - Julian*woodland, Julian*semi-natural

model3a <- glmmTMB(shannon_log ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) + 
                     scale(julian_day)*scale(woodland_prop) + 
                     scale(julian_day)*scale(semi_nat_prop) +
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 216.7
  
summary(model3a)

# check_model(model3)

```

### 2024

```{r}

# Model Shannon index vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3b <- glmmTMB(shannon_log ~ (scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop))^2 + 
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_24)

# Full model - AIC 215.0
# No significant interactions 

model3b <- glmmTMB(shannon_log ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) + 
                    (1 | farm), ziformula=~1, data=dung_beetle_q1_24)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 210.1
  
summary(model3b)

# check_model(model3)

```

# Simpson

```{r}

# Look at log transformation.

dung_beetle_q2 <- dung_beetle %>% drop_na(q_2_simpson)
dung_beetle_q2$simpson_log <- log(dung_beetle_q2$q_2_simpson)

dung_beetle_q2_22 <- dung_beetle_q2 %>% filter(year == '2022')
dung_beetle_q2_24 <- dung_beetle_q2 %>% filter(year == '2024')

plot(fitdist(dung_beetle_q2$simpson_log,"norm"))

```

### 2022

```{r}

# Model Simpson index vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4a <- glmmTMB(simpson_log ~ (scale(julian_day) + 
                                    scale(woodland_prop) + 
                                    scale(ag_prop) + 
                                    scale(semi_nat_prop))^2 + 
                     (1 | farm), ziformula=~1, data=dung_beetle_q2_22)

# Full model - AIC 197.7
# Significant interactions - Julian*woodland, Julian*semi-nat

model4a <- glmmTMB(simpson_log ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) + 
                     scale(julian_day)*scale(semi_nat_prop) +
                     scale(julian_day)*scale(woodland_prop) +
                    (1 | farm), ziformula=~1, data=dung_beetle_q2_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 195.2

summary(model4a)

# check_model(model4)

```

### 2024

```{r}

# Model Simpson index vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4b <- glmmTMB(simpson_log ~ (scale(julian_day) + 
                                    scale(woodland_prop) + 
                                    scale(ag_prop) + 
                                    scale(semi_nat_prop))^2 + 
                     (1 | farm), ziformula=~1, data=dung_beetle_q2_24)

# Full model - AIC 192.0
# No significant interactions 

model4b <- glmmTMB(simpson_log ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) +
                    (1 | farm), ziformula=~1, data=dung_beetle_q2_24)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 187.5

summary(model4b)

# check_model(model4)

```
# Native species abundance

```{r}

plot(fitdist(dung_beetle$native_species_abundance,"pois"))

```

### 2022 

```{r}

# Model native species abundance vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model5a <- glmer.nb(native_species_abundance ~ (scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop))^2 + 
                      (1 | farm), data = dung_beetle_22)

# Full model - AIC 536.3
# Significant interactions - Julian*woodland, Julian*semi-nat

model5a <- glmer.nb(native_species_abundance ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) +
                     scale(julian_day)*scale(semi_nat_prop) +
                     scale(julian_day)*scale(woodland_prop) +
                    (1 | farm), data=dung_beetle_22)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 530.4
# When I tried to use season here as an interaction term with the landscape variables, the significant interactions were lost. 

summary(model5a)

# check_model(model5)

```

### 2024

```{r}

# Model native species abundance vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model5b <- glmer.nb(native_species_abundance ~ (scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop))^2 + 
                      (1 | farm), data = dung_beetle_24)

# Full model - AIC 695.8
# Significant interactions - woodland*ag

model5b <- glmer.nb(native_species_abundance ~ scale(julian_day) + 
                                   scale(woodland_prop) + 
                                   scale(ag_prop) + 
                                   scale(semi_nat_prop) +
                     scale(ag_prop)*scale(woodland_prop) +
                    (1 | farm), data=dung_beetle_24)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 692.4

summary(model5b)

# check_model(model5)

```

# Native species richness

```{r}

plot(fitdist(dung_beetle$native_species_richness,"pois"))

```

### 2022

```{r}

# Model native species richness vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model6a <- glmer(native_species_richness ~ (scale(julian_day) + 
                                             scale(woodland_prop) + 
                                             scale(ag_prop) + 
                                             scale(semi_nat_prop))^2 + 
                  (1 | farm), data = dung_beetle_22, family = poisson)

# Full model - AIC 384.8
# No significant interactions

model6a <- glmer(native_species_richness ~ scale(julian_day) + 
                                             scale(woodland_prop) + 
                                             scale(ag_prop) + 
                                             scale(semi_nat_prop) + 
                  (1 | farm), data = dung_beetle_22, family = poisson)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 383.2

summary(model6a)

# check_model(model6)

```

### 2024

```{r}

# Model native species richness vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model6b <- glmer(native_species_richness ~ (scale(julian_day) + 
                                             scale(woodland_prop) + 
                                             scale(ag_prop) + 
                                             scale(semi_nat_prop))^2 + 
                  (1 | farm), data = dung_beetle_24, family = poisson)

# Full model - AIC 406.3
# No significant interactions

model6b <- glmer(native_species_richness ~ scale(julian_day) + 
                                             scale(woodland_prop) + 
                                             scale(ag_prop) + 
                                             scale(semi_nat_prop) + 
                  (1 | farm), data = dung_beetle_24, family = poisson)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 399.3

summary(model6b)

# check_model(model6)

```

# Native species proportion

### 2022

```{r}

# Model native species proportion vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7a <- glmmTMB(native_species_proportion ~ (scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop))^2 + 
                     (1 | farm), data = dung_beetle_22, family=ordbeta)

# Full model - AIC 207.6
# No significant interactions

model7a <- glmmTMB(native_species_proportion ~ scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop) + 
                     (1 | farm), data = dung_beetle_22, family=ordbeta)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 201.2

summary(model7a)

# check_model(model7)

```

# 2024

```{r}

# Model native species proportion vs. day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7b <- glmmTMB(native_species_proportion ~ (scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop))^2 + 
                     (1 | farm), data = dung_beetle_24, family=ordbeta)

# Full model - AIC 68.6
# No significant interactions

model7b <- glmmTMB(native_species_proportion ~ scale(julian_day) + 
                                                  scale(woodland_prop) + 
                                                  scale(ag_prop) + 
                                                  scale(semi_nat_prop) + 
                     (1 | farm), data = dung_beetle_24, family=ordbeta)

# Model keeping the significant interactions of the global model. 
# Simplified model - AIC 60.9

summary(model7b)

# check_model(model7)

```




