---
title: "dung_beetle_landscape"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(fitdistrplus)
library(lme4)
library(DHARMa)
library(rsq)
library(effects)
library(marginaleffects)
library(glmmTMB)
library(performance)
library(insight)

```

Read in data frame - landscape data pulled from USDA CDL at 1000m radius around each trapping point. Convert data types. 

All landscape data is pulled from the USDA CDL. Agriculture includes all annual and perennial crops. Woodland includes all forested habitat + shrubland. Semi-natural habitat includes pastures and grasslands. 

```{r}

dung_beetle <- read.delim("Data/diversity_landscape.csv", sep = ",")

dung_beetle <- dung_beetle %>%
  mutate(date = as.Date(date, format = "%m/%d")) %>%
  mutate(farm = as.factor(farm))
  
dung_beetle$julian_date <- format(dung_beetle$date, "%j")

dung_beetle <- dung_beetle %>%
  mutate(julian_date = as.numeric(julian_date))

head(dung_beetle)

```

# Total abundance 

All models include year, Julian date, woodland proportion (forests, shrublands), agriculture proportion (all agriculture types), and semi-natural habitat proportion as fixed effects and farm as a random effect. 

Depending on what you find interesting in this, we can play around with model selection and drop some variables.

```{r}

# Check distributions. 

plot(fitdist(dung_beetle$total_abundance,"nbinom"))

```

```{r}

# Model total abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model1 <- glmer.nb(total_abundance ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle)

summary(model1)

# check_model(model1)

```

# Richness

```{r}

plotdist(dung_beetle$q_0_richness, histo = TRUE, demp = TRUE)
plot(fitdist(dung_beetle$q_0_richness,"pois"))

```

```{r}

# Model richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model2 <- glmer(q_0_richness ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family=poisson)

summary(model2)

# check_model(model2)

```

# Shannon

```{r}

# Look at log transformation.

dung_beetle_q1 <- dung_beetle %>% drop_na(q_1_shannon)
dung_beetle_q1$shannon_log <- log(dung_beetle_q1$q_1_shannon)

plot(fitdist(dung_beetle_q1$shannon_log,"norm"))

```

```{r}

# Model Shannon index vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3 <- glmmTMB(shannon_log ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), ziformula=~1, data=dung_beetle_q1)
  
summary(model3)

# check_model(model3)

```

# Simpson

```{r}

# Look at log transformation.

dung_beetle_q2 <- dung_beetle %>% drop_na(q_2_simpson)
dung_beetle_q2$simpson_log <- log(dung_beetle_q2$q_2_simpson)

plot(fitdist(dung_beetle_q2$simpson_log,"norm"))

```

```{r}

# Model Simpson index vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4 <- glmmTMB(simpson_log ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), ziformula=~1, data=dung_beetle_q2)

summary(model4)

# check_model(model4)

```

# Native species abundance

```{r}

plot(fitdist(dung_beetle$native_species_abundance,"pois"))

```

```{r}

# Model native species abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model5 <- glmer(native_species_abundance ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family = poisson)

summary(model5)

# check_model(model5)

```

# Native species richness

```{r}

plot(fitdist(dung_beetle$native_species_richness,"pois"))

```

```{r}

# Model native species richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model6 <- glmer(native_species_richness ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family = poisson)

summary(model6)

# check_model(model6)

```

# Native species proportion


```{r}

# Model native species proportion vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7 <- glmmTMB(native_species_proportion ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family=ordbeta)

summary(model7)

# check_model(model7)

```
