---
title: "dung_beetle_landscape"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(fitdistrplus)
library(lme4)
library(DHARMa)
library(rsq)
library(effects)
library(marginaleffects)
library(glmmTMB)
library(performance)
library(insight)
library(MuMIn)

```

Read in data frame - landscape data pulled from USDA CDL at 1000m radius around each trapping point. Convert data types. 

All landscape data is pulled from the USDA CDL. Agriculture includes all annual and perennial crops. Woodland includes all forested habitat + shrubland. Semi-natural habitat includes pastures and grasslands. 

```{r}

dung_beetle <- read.delim("Data/diversity_landscape.csv", sep = ",")

dung_beetle <- dung_beetle %>%
  mutate(date = as.Date(date, format = "%Y-%m-%d")) %>%
  mutate(farm = as.factor(farm)) %>%
  mutate(season = as.factor(season))

head(dung_beetle)

```

Divide data by year. 

```{r}

dung_beetle_22 <- dung_beetle %>% filter(year == '2022')
dung_beetle_24 <- dung_beetle %>% filter(year == '2024')

```

# Total abundance 

All models include Julian date, woodland proportion (forests, shrublands), agriculture proportion (all agriculture types), and semi-natural habitat proportion as fixed effects and farm as a random effect. For each response variable, there is a model for each year. 

```{r}

# Check distributions. 
plot(fitdist(dung_beetle_22$total_abundance,"nbinom"))
plot(fitdist(dung_beetle_24$total_abundance,"nbinom"))

```

### 2022

```{r}

# Model total abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model1a <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_22, 
                    na.action='na.fail')

# Full model - AIC 1474.4
# Only Julian day and landscape interactions were significant, no landscape-landscape interactions.

model1a_dredge <- dredge(model1a)
summary(get.models(model1a_dredge, 1)[[1]])

# Top model from dredge retained just Julian day, woodland prop, and their interaction. AIC - 1469.7

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1472.2

model1a <- glmer.nb(total_abundance ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) + 
                      scale(julian_day)*scale(woodland_prop) + 
                      scale(julian_day)*scale(ag_prop) + 
                      scale(julian_day)*scale(semi_nat_prop) + 
                      (1 | farm), 
                    data = dung_beetle_22)

summary(model1a)

# check_model(model1a)

```

### 2024

```{r}

# Model total abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model1b <- glmer.nb(total_abundance ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_24, 
                    na.action='na.fail')

# Full model - AIC 1317.1
# Significant interactions - Julian day * prop_ag, woodland_prop*ag_prop.

model1b_dredge <- dredge(model1b)
summary(get.models(model1b_dredge, 1)[[1]])

# Top model from dredge retained ag prop, Julian day, semi-nat prop, woodland prop, and ag_prop interactions with all three. AIC - 1312.3.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 1319.9

model1b <- glmer.nb(total_abundance ~ scale(julian_day) + 
                      scale(woodland_prop) + 
                      scale(ag_prop) + 
                      scale(semi_nat_prop) + 
                      scale(julian_day)*scale(ag_prop) + 
                      scale(woodland_prop)*scale(ag_prop) +
                      (1 | farm), 
                    data = dung_beetle_24)

summary(model1b)

# check_model(model1b)

```

# Richness

```{r}

plot(fitdist(dung_beetle_22$q_0_richness,"pois"))
plot(fitdist(dung_beetle_24$q_0_richness,"pois"))

```

### 2022 

```{r}

# Model richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model2a <- glmer(q_0_richness ~ (scale(julian_day) +
                      scale(woodland_prop) +
                      scale(ag_prop) +
                      scale(semi_nat_prop))^2 +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

# Full model - AIC 725.4
# No significant interactions. Only Julian day is significant.

model2a_dredge <- dredge(model2a)
summary(get.models(model2a_dredge, 1)[[1]])

# Top model from dredge retained Julian day and semi-nat prop. AIC - 716.6.

# Model keeping the significant effects of the global model. 
# Simplified model - AIC 718.5

model2a <- glmer(q_0_richness ~ scale(julian_day) +
                      (1 | farm), 
                    data = dung_beetle_22, family='poisson',
                    na.action='na.fail')

summary(model2a)

# check_model(model2)

```

# Shannon

```{r}

# Look at log transformation.

dung_beetle_q1 <- dung_beetle %>% drop_na(q_1_shannon)
dung_beetle_q1$shannon_log <- log(dung_beetle_q1$q_1_shannon)

plot(fitdist(dung_beetle_q1$shannon_log,"norm"))

```

```{r}

# Model Shannon index vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model3 <- glmmTMB(shannon_log ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), ziformula=~1, data=dung_beetle_q1)
  
summary(model3)

# check_model(model3)

```

# Simpson

```{r}

# Look at log transformation.

dung_beetle_q2 <- dung_beetle %>% drop_na(q_2_simpson)
dung_beetle_q2$simpson_log <- log(dung_beetle_q2$q_2_simpson)

plot(fitdist(dung_beetle_q2$simpson_log,"norm"))

```

```{r}

# Model Simpson index vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

# Zero inflated model.

model4 <- glmmTMB(simpson_log ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), ziformula=~1, data=dung_beetle_q2)

summary(model4)

# check_model(model4)

```

# Native species abundance

```{r}

plot(fitdist(dung_beetle$native_species_abundance,"pois"))

```

```{r}

# Model native species abundance vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model5 <- glmer.nb(native_species_abundance ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle)

summary(model5)

# check_model(model5)

```

# Native species richness

```{r}

plot(fitdist(dung_beetle$native_species_richness,"pois"))

```

```{r}

# Model native species richness vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model6 <- glmer(native_species_richness ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family = poisson)

summary(model6)

# check_model(model6)

```

# Native species proportion


```{r}

# Model native species proportion vs. year, day of year, prop woodland, prop ag, prop semi-natural (and all two-way interactions). Farm as random variable. 

model7 <- glmmTMB(native_species_proportion ~ (scale(year) + scale(julian_date) + scale(woodland_prop) + 
                     scale(ag_prop) + scale(semi_nat_prop))^2 + (1 | farm), data = dung_beetle, family=ordbeta)

summary(model7)

# check_model(model7)

```
