---
title: "Dung Beetle CDL Processing"
author: "Chloe Cho"
date: "2022-12-07"
output: pdf_document
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(janitor)

```

Data upload--the QGIS output at 4 different scales and the 2021 New York CDL Metadata.

```{r}

CDL_Metadata_NY <- read.delim("../Spotted_Wing_Drosophila/CDL_Metadata_2021_NY.csv", sep = ",")
CDL_250_Dung_Beetle <- read.delim("QGIS/dung_beetle_250m.csv", sep = ",")
CDL_500_Dung_Beetle <- read.delim("QGIS/dung_beetle_500m.csv", sep = ",")
CDL_750_Dung_Beetle <- read.delim("QGIS/dung_beetle_750m.csv", sep = ",")
CDL_1000_Dung_Beetle <- read.delim("QGIS/dung_beetle_1000m.csv", sep = ",")

```

Formatting the metadata so that it can be merged with the QGIS output files--the CDL number needs to have "Value" written in front of it so that it can match.

```{r}

CDL_Metadata_NY <- CDL_Metadata_NY %>% 
  mutate(cdl_code = paste("Value", cdl_number, sep = "_"))

```

Merging QGIS outputs with the metadata so that the crops are displayed by name not value.

```{r}

CDL_250_w_crops_Dung_Beetle <- CDL_250_Dung_Beetle %>% 
  select(Name, Value_1:Value_195) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_500_w_crops_Dung_Beetle <- CDL_500_Dung_Beetle %>% 
  select(Name, Value_1:Value_195) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_750_w_crops_Dung_Beetle <- CDL_750_Dung_Beetle %>% 
  select(Name, Value_1:Value_195) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_1000_w_crops_Dung_Beetle <- CDL_1000_Dung_Beetle %>% 
  select(Name, Value_1:Value_195) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

```

Grouping crops to create broad landscape categories - 250m.

```{r}

CDL_250_Summary_Dung_Beetle <- CDL_250_w_crops_Dung_Beetle %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_250 = ((corn + soybeans + winter_wheat + oats + alfalfa + buckwheat + fallow_idle_cropland) / Total),
        PAST_250 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
        NAT_FOR_250 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
        NAT_OPEN_250 = ((clover_wildflowers + developed_open_space + herbaceous_wetlands) / Total),
        DEV_250 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren) / Total),
        NAT_250 = NAT_FOR_250 + NAT_OPEN_250,  
        NAT_PAST_250 = PAST_250 + NAT_OPEN_250, 
        AG_PAST_250 = AG_250 + PAST_250
        ) %>% 
    select(na, AG_250:AG_PAST_250)

```

Grouping crops to create broad landscape categories - 500m.

```{r}

CDL_500_Summary_Dung_Beetle <- CDL_500_w_crops_Dung_Beetle %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_500 = ((corn + soybeans + winter_wheat + oats + alfalfa + buckwheat + fallow_idle_cropland) / Total),
        PAST_500 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
        NAT_FOR_500 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
        NAT_OPEN_500 = ((clover_wildflowers + developed_open_space + herbaceous_wetlands) / Total),
        DEV_500 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren) / Total),
        NAT_500 = NAT_FOR_500 + NAT_OPEN_500,  
        NAT_PAST_500 = PAST_500 + NAT_OPEN_500, 
        AG_PAST_500 = AG_500 + PAST_500
        ) %>% 
    select(na, AG_500:AG_PAST_500)

```

Grouping crops to create broad landscape categories - 750m.

```{r}

CDL_750_Summary_Dung_Beetle <- CDL_750_w_crops_Dung_Beetle %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_750 = ((corn + soybeans + winter_wheat + oats + alfalfa + buckwheat + fallow_idle_cropland) / Total),
        PAST_750 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
        NAT_FOR_750 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
        NAT_OPEN_750 = ((clover_wildflowers + developed_open_space + herbaceous_wetlands) / Total),
        DEV_750 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren) / Total),
        NAT_750 = NAT_FOR_750 + NAT_OPEN_750,  
        NAT_PAST_750 = PAST_750 + NAT_OPEN_750, 
        AG_PAST_750 = AG_750 + PAST_750
        ) %>% 
    select(na, AG_750:AG_PAST_750)

```

Grouping crops to create broad landscape categories - 1000m.

```{r}

CDL_1000_Summary_Dung_Beetle <- CDL_1000_w_crops_Dung_Beetle %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_1000 = ((corn + soybeans + winter_wheat + oats + alfalfa + buckwheat + fallow_idle_cropland) / Total),
        PAST_1000 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
        NAT_FOR_1000 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
        NAT_OPEN_1000 = ((clover_wildflowers + developed_open_space + herbaceous_wetlands) / Total),
        DEV_1000 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren) / Total),
        NAT_1000 = NAT_FOR_1000 + NAT_OPEN_1000,  
        NAT_PAST_1000 = PAST_1000 + NAT_OPEN_1000, 
        AG_PAST_1000 = AG_1000 + PAST_1000
        ) %>% 
    select(na, AG_1000:AG_PAST_1000)

```

Joining the four different scales.

```{r}

Final_CDL_Dung_Beetle_2021 <- CDL_250_Summary_Dung_Beetle %>% 
  left_join(CDL_500_Summary_Dung_Beetle) %>% 
  left_join(CDL_750_Summary_Dung_Beetle) %>% 
  left_join(CDL_1000_Summary_Dung_Beetle) # %>% 
  # rename(Site = na) %>% 
  #filter(Site %in% c("Indian_Creek_B1", "CU_Orchards_B", "Stick_and_Stone_B", "West_Haven_B", "Grisamore_B", "Silver_Queen_B", "Shared_Roots_B2", "Cassim_B","Buried_Treasures_B", "Research_North_B2","Fellenz_B","Full_Circle_B","Sampson_B", "Remembrance_B")) %>% 
  #mutate(Site = recode(Site, "Indian_Creek_B1" = "IC", "CU_Orchards_B" = "CO", "Stick_and_Stone_B" = "SS", "West_Haven_B" = "WH", "Grisamore_B" = "GR", "Silver_Queen_B" = "SQ", "Shared_Roots_B2" = "SR", "Cassim_B" = "CA", "Buried_Treasures_B" = "BT", "Research_North_B2" = "RN", "Fellenz_B" = "FE", "Full_Circle_B" = "FC", "Sampson_B" = "SA", "Remembrance_B" = "RE"))
  
```
Writing the csv file.

```{r}

# write.csv(Final_CDL_Dung_Beetle_2021, file = "QGIS/Final_CDL_Dung_Beetle_2021.csv")

```
