---
title: "NYS IPM Sweet Corn Long-Term Pest Data"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(scales)
library(sf)
library(mapview)

```

## Introduction

NYS IPM sweet corn pheromone trapping dataset 1993-2022. Data was initially used as a monitoring tool to inform growers about corn pest populations. 

**LINKS/RESOURCES**

- [EDA Slide Deck](https://cornell.app.box.com/integrations/googledss/openGoogleEditor?fileId=1112400398858&trackingId=3#slide=id.p)
- [Pest population dynamics are related to a continental overwintering gradient](https://doi.org/10.1073/pnas.2203230119)
- [Pest Data Sheets](https://sweetcorn.nysipm.cornell.edu/)

**LIMITATIONS & NOTES**

- GPS coordinates are not precise because traps moved around from year to year depending on where sweet corn was planted. Some farms are much larger than the typical 1000m radius that we use. 
- The timing of trap placement varied from year to year, shifted earlier for certain pests when they began to emerge earlier. 
- Blanks are NAs (no data collected since traps were not set up yet), zeros are actual observations of no pest at that sampling event. 

**PESTS**

- European Corn Borer (ECB) (E and Z strains for sex pheromones)
- Corn Earworm (CEW)
- Western Bean Cutworm (WBC)
- Fall Armyworm (FAW)

## Read Data

Read in csv file. Columns Site, USDA Hardiness Zone, Latitude, Longitude, Year, Week, Date, Day, ECB.E, ECB.Z, CEW, FAW, and WBC. Each row is a sampling event at a farm. 

Melt data frame to create a row for each observation, creating a column for the pest name and a column for the pest count. 

```{r}

sweet_corn_pest <- read.delim("NYSIPM_Sweet_Corn_1993_2022.csv", sep = ",")

sweet_corn_pest <- sweet_corn_pest %>% 
  mutate(Date = as.Date(Date, format = '%m/%d/%y')) %>%
  mutate(Site = as.factor(Site)) %>%
  mutate(USDA.hardiness.Zone = as.factor(USDA.hardiness.Zone)) %>%
  mutate(new_col = format(Date, "%j"), .after = Date) %>%
  rename(Day = new_col)

sweet_corn_pest_long <- melt(sweet_corn_pest, id.vars = c("Site", "USDA.hardiness.Zone", "Lat", "Long", "Year", "Week", "Date", "Day"), measure.vars = c("ECB.E", "ECB.Z", "CEW", "FAW", "WBC"), variable.name = 'Pest', value.name = 'Count')

head(sweet_corn_pest_long)

```

## Site Data

Upload csv with latitude and longitude for all sites. There are 89 unique values for sites. 

```{r}

sites <- read.delim("NYSIPM_Sweet_Corn_1993_2022_Sites.csv", sep = ",")

sites <- sites %>% 
  mutate(Site = as.factor(Site)) %>%
  select(-c('X', 'X.1', 'X.2', 'X.3', 'X.4', 'X.5', 'X.6', 'X.7'))

length(levels(sites$Site))

head(sites)

```

## Plot Sites

Explore the north-south distribution of the monitoring sites. 

```{r}

sites_with_coord <- sites %>% drop_na()

mapview(sites_with_coord, xcol = "Long.Decimal", ycol = "Lat.Decimal", crs = 4269, grid = FALSE)

```

## Exploratory Data Analysis

Create initial visualizations of the pest count data. Exploring differences in years, species, and sites. 

**Pest Counts 1993-2022, Faceted by Species**

Each species shows different patterns in abundance over time. ECB has decreased over time, while CEW, FAW, and WBC have increased.  

```{r}

sweet_corn_pest_long %>%
  ggplot(aes(Date, Count)) + 
  geom_line() +
  ggtitle('Pest Counts 1993-2022') +
  facet_wrap(~ Pest)

```

**ECB_E Count, Faceted by Year**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'ECB.E') %>%
  ggplot(aes(Day, Count)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('ECB_E Counts 1993-2022') +
  facet_wrap(~ Year)

```

**ECB_Z Count, Faceted by Year**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'ECB.Z') %>%
  ggplot(aes(Day, Count)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('ECB_Z Counts 1993-2022') +
  facet_wrap(~ Year)

```

**CEW Count, Faceted by Year**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'CEW') %>%
  ggplot(aes(Day, Count)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('CEW Counts 1993-2022') +
  facet_wrap(~ Year)

```

**FAW Count, Faceted by Year**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'FAW') %>%
  ggplot(aes(Day, Count)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('FAW Counts 1993-2022') +
  facet_wrap(~ Year)

```

**WBC Count, Faceted by Year**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'WBC') %>%
  ggplot(aes(Day, Count)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('WBC Counts 1993-2022') +
  facet_wrap(~ Year)

```

**All Pest Counts, Faceted by Yearr**

```{r fig.height=8, fig.width=12}

sweet_corn_pest_long %>%
  ggplot(aes(Day, Count, col = Pest)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('Sweet Corn Pest Counts 1993-2022') +
  facet_wrap(~ Year)

```

**Sweet Corn Pest Count, 1993-1995**

```{r}

sweet_corn_pest_long %>%
  dplyr::filter(((Year >= 1993) & (Year <= 1995))) %>%
  ggplot(aes(Date, Count, col = Pest)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('Sweet Corn Pest Counts 1993-1995')

```

**Sweet Corn Pest Count, 2020-2022**

```{r}

sweet_corn_pest_long %>%
  dplyr::filter(((Year >= 2020) & (Year <= 2022))) %>%
  ggplot(aes(Date, Count, col = Pest)) + 
  geom_line() +
  geom_point(size = 0.25) +
  ggtitle('Sweet Corn Pest Counts 2020-2022')

```

```{r fig.height=12, fig.width=14}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'ECB.E') %>%
  ggplot(aes(Date, Count)) + 
  geom_line(size = 1) +
  geom_point(size = 0.5) +
  ggtitle('ECB_E Counts 1993-2022 by Site') +
  facet_wrap(~ Site)

```

```{r fig.height=12, fig.width=14}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'ECB.Z') %>%
  ggplot(aes(Date, Count)) + 
  geom_line(size = 1) +
  geom_point(size = 0.5) +
  ggtitle('ECB_Z Counts 1993-2022 by Site') +
  facet_wrap(~ Site)

```

```{r fig.height=12, fig.width=14}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'CEW') %>%
  ggplot(aes(Date, Count)) + 
  geom_line(size = 1) +
  geom_point(size = 0.5) +
  ggtitle('CEW Counts 1993-2022 by Site') +
  facet_wrap(~ Site)

```

```{r fig.height=12, fig.width=14}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'FAW') %>%
  ggplot(aes(Date, Count)) + 
  geom_line(size = 1) +
  geom_point(size = 0.5) +
  ggtitle('FAW Counts 1993-2022 by Site') +
  facet_wrap(~ Site)

```

```{r fig.height=12, fig.width=14}

sweet_corn_pest_long %>%
  dplyr::filter(Pest == 'WBC') %>%
  ggplot(aes(Date, Count)) + 
  geom_line(size = 1) +
  geom_point(size = 0.5) +
  ggtitle('WBC Counts 1993-2022 by Site') +
  facet_wrap(~ Site)

```

```{r}

sweet_corn_pest_long %>%
  replace(is.na(sweet_corn_pest_long), 0) %>%
  dplyr::filter(Pest == 'ECB.E') %>%
  group_by(Year) %>%
  summarise(Total = sum(Count)) %>%
  ggplot(aes(x = Year, y = Total)) + 
  geom_bar(stat = 'identity') +
  ggtitle('ECB.E Counts 1993-2022')

```

```{r}

sweet_corn_pest_long %>%
  replace(is.na(sweet_corn_pest_long), 0) %>%
  dplyr::filter(Pest == 'ECB.Z') %>%
  group_by(Year) %>%
  summarise(Total = sum(Count)) %>%
  ggplot(aes(x = Year, y = Total)) + 
  geom_bar(stat = 'identity') +
  ggtitle('ECB.Z Counts 1993-2022')

```

```{r}

sweet_corn_pest_long %>%
  replace(is.na(sweet_corn_pest_long), 0) %>%
  dplyr::filter(Pest == 'CEW') %>%
  group_by(Year) %>%
  summarise(Total = sum(Count)) %>%
  ggplot(aes(x = Year, y = Total)) + 
  geom_bar(stat = 'identity') +
  ggtitle('CEW Counts 1993-2022')

```

```{r}

sweet_corn_pest_long %>%
  replace(is.na(sweet_corn_pest_long), 0) %>%
  dplyr::filter(Pest == 'FAW') %>%
  group_by(Year) %>%
  summarise(Total = sum(Count)) %>%
  ggplot(aes(x = Year, y = Total)) + 
  geom_bar(stat = 'identity') +
  ggtitle('FAW Counts 1993-2022')

```

```{r}

sweet_corn_pest_long %>%
  replace(is.na(sweet_corn_pest_long), 0) %>%
  dplyr::filter(Pest == 'WBC') %>%
  group_by(Year) %>%
  summarise(Total = sum(Count)) %>%
  ggplot(aes(x = Year, y = Total)) + 
  geom_bar(stat = 'identity') +
  ggtitle('WBC Counts 1993-2022')

```








