---
title: "NYSIPM_Sweet_Corn_Modeling"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(reshape2)
library(scales)
library(fitdistrplus)
library(lme4)

library(Boruta)
library(mlbench)
library(caret)
library(randomForest)

library(xgboost)
library(cvms)
library(caret)
library(caTools)
library(pROC)
library(ROCR)

library(sqldf)
library(lubridate)

```

# Questions


# Data

## NYS IPM Data

### Read & Clean Data 

Data from NYS IPM (Marion Zuefle) for ECB_E, ECB_Z, CEW, FAW, and WBC. 

```{r}

sweet_corn_pest <- read.delim("NYSIPM_Sweet_Corn_1993_2022.csv", sep = ",")

# Format data types.
sweet_corn_pest <- sweet_corn_pest %>% 
  mutate(Date = as.Date(Date, format = '%m/%d/%y')) %>%
  mutate(Site = as.factor(Site)) %>%
  mutate(USDA.hardiness.Zone = as.factor(USDA.hardiness.Zone)) %>%
  mutate(new_col = format(Date, "%j"), .after = Date) %>%
  rename(Day = new_col) %>%
  mutate(Day = as.numeric(Day)) %>%
  mutate(Site = str_replace(Site, "Baldwinsvillie", "Baldwinsville"))

# Create a row for each pest observation. 
sweet_corn_pest_long <- melt(sweet_corn_pest, id.vars = c("Site", "USDA.hardiness.Zone", "Lat", "Long", "Year", "Week", "Date", "Day"), measure.vars = c("ECB.E", "ECB.Z", "CEW", "FAW", "WBC"), variable.name = 'Pest', value.name = 'Count')

head(sweet_corn_pest_long)

```

### NYS Sites

```{r}

sites <- read.delim("NYSIPM_Sweet_Corn_1993_2022_Sites.csv", sep = ",")

length(levels(sites$Site))

sites <- sites %>% 
  mutate(Site = str_replace(Site, "Accord ", "Accord")) %>%
  mutate(Site = str_replace(Site, "PennYan", "Penn Yan")) %>%
  mutate(Site = as.factor(Site))
  

sites <- sites %>%
  dplyr::select(-c('X', 'X.1', 'X.2', 'X.3', 'X.4', 'X.5', 'X.6', 'X.7'))

head(sites)

levels(sites$Site)

```

Add decimal GPS coordinates to table. 

```{r}

sites_decimal_gps <- sites %>%
  dplyr::select(c('Site', 'Lat.Decimal', 'Long.Decimal'))

sweet_corn_pest_full <- sweet_corn_pest_long %>%
  left_join(sites_decimal_gps, by = c("Site" = "Site"))

head(sweet_corn_pest_full)

```

Add proportion corn in landscape to sites. 

```{r}

corn_5km_2002 <- read.delim("Landscape/final_cdl_corn_5km_2002.csv", sep = ",") %>%
  mutate(year = 2002) %>%
  dplyr::select(c(site, prop_corn, year)) %>%
  mutate(site = str_replace(site, "_", " "))

corn_5km_2012 <- read.delim("Landscape/final_cdl_corn_5km_2012.csv", sep = ",") %>%
  mutate(year = 2012) %>%
  dplyr::select(c(site, prop_corn, year)) %>%
  mutate(site = str_replace(site, "_", " "))

corn_5km_2022 <- read.delim("Landscape/final_cdl_corn_5km_2022.csv", sep = ",") %>%
  mutate(year = 2022) %>%
  dplyr::select(c(site, prop_corn, year)) %>%
  mutate(site = str_replace(site, "_", " "))

```

```{r}

set.seed(42)

sweet_corn_pest_features <- sweet_corn_pest_full %>%
  dplyr::select(c('Site', 'Lat.Decimal', 'Long.Decimal', 'Year', 'Week', 'Date', 'Day', 'Pest', 'Count')) %>%
  na.omit(subset(sweet_corn_pest_full, select = c('Site', 'Lat.Decimal', 'Long.Decimal', 'Year', 'Week', 'Date', 'Day', 'Pest', 'Count'))) 

cdl_2002 <- sqldf('SELECT * 
  FROM sweet_corn_pest_features
  LEFT JOIN corn_5km_2002 
  ON sweet_corn_pest_features.Site = corn_5km_2002.site 
  WHERE sweet_corn_pest_features.Year >= 1993 
  AND sweet_corn_pest_features.Year <= 2002') %>%
  dplyr::select(-c(site, year))

cdl_2012 <- sqldf('SELECT * 
  FROM sweet_corn_pest_features
  LEFT JOIN corn_5km_2012 
  ON sweet_corn_pest_features.Site = corn_5km_2012.site 
  WHERE sweet_corn_pest_features.Year >= 2003 
  AND sweet_corn_pest_features.Year <= 2012') %>%
  dplyr::select(-c(site, year))

cdl_2022 <- sqldf('SELECT * 
  FROM sweet_corn_pest_features
  LEFT JOIN corn_5km_2022 
  ON sweet_corn_pest_features.Site = corn_5km_2022.site 
  WHERE sweet_corn_pest_features.Year >= 2013 
  AND sweet_corn_pest_features.Year <= 2022') %>%
  dplyr::select(-c(site, year))

sweet_corn_pest_features <- bind_rows(cdl_2002, cdl_2012, cdl_2022)

```

Add climate data. 

```{r}

climate_data <- read.delim("../../Desktop/Cornell/Long_Term_Pest_Data/Climate_1993_2022.csv", sep = ",") 

climate_data <- climate_data %>%
  mutate(Date = as.Date(climate_data$date, format = '%Y-%m-%d')) %>%
  mutate(Week = lubridate::isoweek(ymd(Date))) %>%
  mutate(Year = lubridate::isoyear(ymd(Date))) %>%
  dplyr::select(-c(date))

# Minimum temperature over week (prism). 

min_temp <- climate_data %>%
  group_by(Site, Year, Week) %>%
  summarise_at(vars(tmin_prism), .funs = min)

# Maximum temperature over week (prism). 

max_temp <- climate_data %>%
  group_by(Site, Year, Week) %>%
  summarise_at(vars(tmax_prism), .funs = max)

# Average temperature over week. 

avg_temp <- climate_data %>%
  group_by(Site, Year, Week) %>%
  summarise_at(vars(tmin_prism, tmax_prism), .funs = mean) %>% 
  rowwise() %>%
  mutate(Avg_Temp = mean(c(tmin_prism, tmax_prism))) %>%
  dplyr::select(-c(tmin_prism, tmax_prism))

# Average precipitation over week.

total_precip <- climate_data %>%
  group_by(Site, Year, Week) %>%
  summarise_at(vars(pr_prism), .funs = sum)

```

# Feature Selection 

Testing a few different kinds of feature selection with current variables. Will add more as we get climate and soil data. 

Boruta feature selection. Read about Boruta [here](https://towardsdatascience.com/boruta-explained-the-way-i-wish-someone-explained-it-to-me-4489d70e154a).

```{r}

ecb_e_features <- sweet_corn_pest_features %>%
  dplyr::filter(Pest == 'ECB.E') %>%
  dplyr::select(-c(Pest))

boruta_ecb_e <- Boruta(Count ~ ., data = na.exclude(ecb_e_features), doTrace = 2, maxRuns = 500)
print(boruta_ecb_e)

plot(boruta_ecb_e, las = 2, cex.axis = 0.7)

ecb_z_features <- sweet_corn_pest_features %>%
  dplyr::filter(Pest == 'ECB.Z') %>%
  dplyr::select(-c(Pest))

boruta_ecb_z <- Boruta(Count ~ ., data = na.exclude(ecb_z_features), doTrace = 2, maxRuns = 500)
print(boruta_ecb_e)

plot(boruta_ecb_z, las = 2, cex.axis = 0.7)

cew_features <- sweet_corn_pest_features %>%
  dplyr::filter(Pest == 'CEW') %>%
  dplyr::select(-c(Pest)) %>%
  mutate(Threshold = case_when(
    Count <= 1 ~ 0,
    Count > 1 ~ 1
    ))
  

boruta_cew <- Boruta(Count ~ ., data = na.exclude(cew_features), doTrace = 2, maxRuns = 500)
print(boruta_cew)

plot(boruta_cew, las = 2, cex.axis = 0.7)

faw_features <- sweet_corn_pest_features %>%
  dplyr::filter(Pest == 'FAW') %>%
  dplyr::select(-c(Pest))

boruta_faw <- Boruta(Count ~ ., data = na.exclude(faw_features), doTrace = 2, maxRuns = 500)
print(boruta_faw)

plot(boruta_faw, las = 2, cex.axis = 0.7)

wbc_features <- sweet_corn_pest_features %>%
  dplyr::filter(Pest == 'WBC') %>%
  dplyr::select(-c(Pest))

boruta_wbc <- Boruta(Count ~ ., data = na.exclude(wbc_features), doTrace = 2, maxRuns = 500)
print(boruta_wbc)

plot(boruta_wbc, las = 2, cex.axis = 0.7)


```

Run a random forest to select which features are most important. 

```{r}

ecb_e_rf <- randomForest(Count ~ Lat.Decimal + Long.Decimal + Year + Day + prop_corn, data = ecb_e_features, ntree = 500, na.action = na.exclude)
importance(ecb_e_rf)

ecb_z_rf <- randomForest(Count ~ Lat.Decimal + Long.Decimal + Year + Day + prop_corn, data = ecb_z_features, ntree = 500, na.action = na.exclude)
importance(ecb_z_rf)

cew_rf <- randomForest(Count ~ Lat.Decimal + Long.Decimal + Year + Day + prop_corn, data = cew_features, ntree = 500, na.action = na.exclude)
importance(cew_rf)

faw_rf <- randomForest(Count ~ Lat.Decimal + Long.Decimal + Year + Day + prop_corn, data = faw_features, ntree = 500, na.action = na.exclude)
importance(faw_rf)

wbc_rf <- randomForest(Count ~ Lat.Decimal + Long.Decimal + Year + Day + prop_corn, data = wbc_features, ntree = 500, na.action = na.exclude)
importance(wbc_rf)

```

# GLMM

## Selecting a Distribution

Negative binomial. 

```{r}

plot(fitdist(c(na.exclude(ecb_e_features$Count)),"nbinom"))

```

Poisson. 

```{r}

plot(fitdist(c(na.exclude(ecb_e_features$Count)),"pois"))

```

By comparing these two graphs, the negative binomial distribution fits the count data better than a Poisson distribution. This will be the distribution used in future models. 

## Running an Initial Model

Running an initial model with just the random effects.

```{r}

initial_model <- glmer.nb(Count ~ (1 | Site), data = sweet_corn_pest_full)
summary(initial_model)

```

## Adding Variables to Model

### ECB_E Model

Running a model with individual predictors, no interactions. 

```{r}

ecb_e_1 <- glmer.nb(Count ~ scale(Lat.Decimal) + scale(Long.Decimal) + scale(Day) + scale(prop_corn) + (1 | Site) + (1 | Year), data = ecb_e_features)
summary(ecb_e_1)

```

### ECB_Z Model

Running a model with individual predictors, no interactions. 

```{r}

ecb_z_1 <- glmer.nb(Count ~ scale(Lat.Decimal) + scale(Long.Decimal) + scale(Day) + scale(prop_corn) + (1 | Site) + (1 | Year), data = ecb_z_features)
summary(ecb_z_1)

```

### CEW Model

Running a model with individual predictors, no interactions. 

```{r}

cew_1 <- glmer.nb(Count ~ scale(Lat.Decimal) + scale(Long.Decimal) + scale(Day) + scale(prop_corn) + (1 | Site) + (1 | Year), data = cew_features)
summary(cew_1)

```

### FAW Model

Running a model with individual predictors, no interactions. 

```{r}

faw_1 <- glmer.nb(Count ~ scale(Lat.Decimal) + scale(Long.Decimal) + scale(Day) + scale(prop_corn) + (1 | Site) + (1 | Year), data = faw_features)
summary(faw_1)

```

### WBC Model

Running a model with individual predictors, no interactions. 

```{r}

wbc_1 <- glmer.nb(Count ~ scale(Lat.Decimal) + scale(Long.Decimal) + scale(Day) + scale(prop_corn)  + (1 | Site) + (1 | Year), data = wbc_features)
summary(wbc_1)

```

# Random Forest Models 

- [Random Forest in R](https://www.statology.org/random-forest-in-r/)

## ECB_E 

```{r}

ecb_e_rf_1 <- randomForest(formula = Count ~ Lat.Decimal + Long.Decimal + Day + Year + prop_corn,
                           data = ecb_e_features, na.action = na.exclude)

ecb_e_rf_1

# Find the number of trees that produce lowest test MSE.
which.min(ecb_e_rf_1$mse)

# Find the RMSE of the best model.
sqrt(ecb_e_rf_1$mse[which.min(ecb_e_rf_1$mse)]) 

# Plot the test MSE by number of trees.
plot(ecb_e_rf_1)

# Produce variable importance plot -  displays the importance of each predictor variable in the final model.
varImpPlot(ecb_e_rf_1)

```

## ECB_Z 

```{r}

ecb_z_rf_1 <- randomForest(formula = Count ~ Lat.Decimal + Long.Decimal + Day + Year + prop_corn,
                           data = ecb_z_features, na.action = na.exclude)

# Display the fitted model. 
ecb_z_rf_1

# Find the number of trees that produce lowest test MSE.
which.min(ecb_z_rf_1$mse)

# Find the RMSE of the best model.
sqrt(ecb_z_rf_1$mse[which.min(ecb_z_rf_1$mse)]) 

# Produce variable importance plot -  displays the importance of each predictor variable in the final model.
varImpPlot(ecb_z_rf_1)

```

## CEW

```{r}

cew_rf_1 <- randomForest(formula = Count ~ Lat.Decimal + Long.Decimal + Day + Year + prop_corn,
                           data = cew_features, na.action = na.exclude)

# Display the fitted model. 
cew_rf_1

# Find the number of trees that produce lowest test MSE.
which.min(cew_rf_1$mse)

# Find the RMSE of the best model.
sqrt(cew_rf_1$mse[which.min(cew_rf_1$mse)])

# Produce variable importance plot -  displays the importance of each predictor variable in the final model.
varImpPlot(cew_rf_1)

```

## FAW

```{r}

faw_rf_1 <- randomForest(formula = Count ~ Lat.Decimal + Long.Decimal + Day + Year + prop_corn,
                           data = faw_features, na.action = na.exclude)

# Display the fitted model. 
faw_rf_1

# Find the number of trees that produce lowest test MSE.
which.min(faw_rf_1$mse)

# Find the RMSE of the best model.
sqrt(faw_rf_1$mse[which.min(faw_rf_1$mse)]) 

# Produce variable importance plot -  displays the importance of each predictor variable in the final model.
varImpPlot(faw_rf_1)

```

## WBC

```{r}

wbc_rf_1 <- randomForest(formula = Count ~ Lat.Decimal + Long.Decimal + Day + Year + prop_corn,
                           data = wbc_features, na.action = na.exclude)

# Display the fitted model. 
wbc_rf_1

# Find the number of trees that produce lowest test MSE.
which.min(wbc_rf_1$mse)

# Find the RMSE of the best model.
sqrt(wbc_rf_1$mse[which.min(wbc_rf_1$mse)]) 

# Produce variable importance plot -  displays the importance of each predictor variable in the final model.
varImpPlot(wbc_rf_1)

```

# XGBoost 

- [XGBoost](https://appsilon.com/r-xgboost/)
- [XGBoost in R](https://www.kaggle.com/code/rtatman/machine-learning-with-xgboost-in-r/notebook)

```{r}

set.seed(42)

cew_features_numeric <- cew_features %>% 
  dplyr::mutate(Date = as.numeric(as.Date(cew_features$Date)-as.Date(0, origin="1899-12-30")))

sample_split <- sample.split(Y = cew_features_numeric$Threshold, SplitRatio = 0.7)

train_set <- subset(x = cew_features_numeric, sample_split == TRUE)
test_set <- subset(x = cew_features_numeric, sample_split == FALSE)

y_train <- as.integer(train_set$Threshold)
y_test <- as.integer(test_set$Threshold)

X_train <- train_set %>% 
  dplyr::select(c(Lat.Decimal, Long.Decimal, Day, Year, prop_corn)) %>%
  as.matrix()

X_test <- test_set %>% 
  dplyr::select(c(Lat.Decimal, Long.Decimal, Day, Year, prop_corn)) %>%
  as.matrix()

dtrain <- xgb.DMatrix(data = X_train, label= y_train)
dtest <- xgb.DMatrix(data = X_test, label= y_test)

```

```{r}

model <- xgboost(data = dtrain, 
                 nround = 10, 
                 objective = "binary:logistic")

pred <- predict(model, dtest)

err <- mean(as.numeric(pred > 0.5) != y_test)
print(paste("test-error=", err))

accuracy <- mean(as.numeric(pred > 0.5) == y_test)
print(paste("test-accuracy=", accuracy))


# Check training accuracy.

pred_train <- predict(model, dtrain)

err_train <- mean(as.numeric(pred_train > 0.5) != y_train)
print(paste("train-error=", err_train))

accuracy_train <- mean(as.numeric(pred > 0.5) == y_test)
print(paste("test-accuracy=", accuracy_train))

# random oversampling
# Smoat and Addison - add noise 

# F1 score 

confusionMatrix(as.factor(as.numeric(pred > 0.5)), as.factor(y_test), mode = "everything", positive = "1")

# better with false positives - optimize with recall - quantify cost 
# optimize to which side they would prefer to lean toward

# ROC AUC 

roc_object <- roc(y_test ~ as.numeric(pred > 0.5), plot = TRUE, print.auc = TRUE)
print(paste("roc auc =", auc(roc_object)))


preds <- prediction(pred, y_test)
plot(performance(preds, measure = "tpr", x.measure = "fpr"))

```

# Time Series

- [Time Series Forecasting in R](https://towardsdatascience.com/a-guide-to-forecasting-in-r-6b0c9638c261)
- [Getting Started with Time Series in R](https://medium.com/@siglimumuni/getting-started-with-time-series-forecasting-in-r-66af90510848)









