---
title: "dung_beetle_rarefaction"
author: "Chloe Cho"
date: "`r Sys.Date()`"
output:
  html_document: default
  pdf_document: default
---

```{r setup, include=FALSE}

knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(janitor)
library(vegan)
library(iNEXT)

```

# Read and Clean Data

```{r}

beetle_counts <- read.delim("../Data/Dung_Beetle_Data.csv", sep = ",")
beetle_counts <- clean_names(beetle_counts)
head(beetle_counts)

```

```{r}

beetle_counts <- beetle_counts %>%
  mutate(non_or_insecticide = tolower(non_or_insecticide)) %>%
  mutate(weather = tolower(weather)) %>%
  mutate(farm = tolower(farm)) %>%
  mutate(active_ingredients = tolower(active_ingredients)) %>%
  mutate(region = tolower(region)) 

head(beetle_counts)

```

```{r}

beetle_counts <- beetle_counts %>%
  mutate(farm = as.factor(farm)) %>%
  mutate(region = as.factor(region)) %>%
  mutate(weather = as.factor(weather)) %>%
  mutate(non_or_insecticide = as.factor(non_or_insecticide)) %>%
  mutate(active_ingredients = as.factor(active_ingredients)) %>%
  mutate(date = as.factor(date)) %>%
  mutate(date = as.Date(date, format="%m/%d/%y"))

```


```{r}

beetle_counts <- beetle_counts %>%
  mutate(non_or_insecticide = case_when(non_or_insecticide == 'non   ' ~ 'non',
                                        non_or_insecticide == 'insecticide' ~ 'insecticide',
                                        non_or_insecticide == 'non' ~ 'non'))

beetle_counts <- beetle_counts %>%
  select(-c(date, region, temp, weather, non_or_insecticide, active_ingredients, gps, histeridae, hydrophilidae, staphylinidae, scarabaeidae, horn_flies, face_flies)) %>%
  rename(site = farm) %>%
  replace(is.na(.), 0)

beetle_counts <- beetle_counts %>% 
  group_by(site) %>% 
  summarise(across(everything(), sum))

farms <- c('chaseholm', 'eisele farm', 'honeyhill', 'johnk farm', 'turner', 'kuipers', 'rugenstein family farm', 'shephard farm', 'wallbridge', 'boone farm')
beetle_counts <- as.data.frame(t(beetle_counts[,-1]))
colnames(beetle_counts) <- farms

beetle_counts <- beetle_counts %>%
  rename(C_N = chaseholm)%>%
  rename(EF_N = `eisele farm`)%>%
  rename(H_N = honeyhill)%>%
  rename(JF_N = `johnk farm`)%>%
  rename(T_N = turner)%>%
  rename(K_I = kuipers)%>%
  rename(RF_I = `rugenstein family farm`)%>%
  rename(SF_I = `shephard farm`)%>%
  rename(W_I = wallbridge) %>%
  rename(BF_I = `boone farm`) 

head(beetle_counts)

```

# Rarefaction Analysis for Abundance-Based Data

Abundance data - summed across the subplots within the locality. 

- n = number of individuals  
- S. obs = observed number of species in the locality. 
- SC = sample coverage (estimated values of sampling completeness for each locality, between 0 and 1)  

```{r}

DataInfo(beetle_counts, datatype = 'abundance')

```

Draw rarefaction curves to see differences between localities. Dotted lines are extrapolated. We can see that the total number of individuals varies greatly between sites. 

```{r}

D_abund <- iNEXT(beetle_counts, datatype = 'abundance')
plot(D_abund)

```

## Standarize to Number of Individuals 

Rarefy the diversities of all localities to the lowest number of individuals in a locality - Turner's (T_N). 

```{r}

D_abund_133 <- iNEXT(beetle_counts, datatype = 'abundance', endpoint = 133)
plot (D_abund_133)

```

Calculate estimated numbers. Column qD contains the estimated diversity for individual localities. 

Orders:  

- q = 0 for species richness  
- q = 1 for Shannon diversity  
- q = 2 for Simpson diversity  

```{r}

est_D_abund <- estimateD (beetle_counts, datatype = 'abundance')
head(est_D_abund)

```

Filter out species richness. 

```{r}

D_individuals <- D_individuals <- est_D_abund$qD[est_D_abund$Order.q == 0]
  
# filter(est_D_abund, Order.q == 0)

#D_individuals %>%
#  select(c(Assemblage, qD))

```

## Standardize to Sample Coverage

Plot the coverage rarefaction curve for each locality. Then plot the high end of the sample coverages. 

Locality with the lowest coverage is Turner, which also had the lowest number of individuals. 

```{r}

plot(D_abund, type = 3)
plot (D_abund, type = 3, xlim = c(.95, 1))

```

Standardize the diversities to the lowest coverage, 0.984688. Filter again by species richness. 

```{r}

est_D_abund_coverage <- estimateD(beetle_counts, datatype = 'abundance', base = 'coverage')
est_D_abund_coverage

D_coverage <- est_D_abund_coverage$qD[est_D_abund_coverage$Order.q == 0]
  
#filter(est_D_abund_coverage, Order.q == 0)

#D_coverage %>%
#  select(c(Assemblage, qD))

```



```{r}

# number of observed species at each locality
D_area <- DataInfo (beetle_counts, datatype = 'abundance')$S.obs 

# add in the estimated species richness under standardization by individuals and sample coverage
D_est <- cbind (D_area, D_individuals, D_coverage)
rownames (D_est) <- DataInfo (beetle_counts, datatype = 'abundance')$Assemblage

```

```{r}

barplot(D_est, beside = T, legend.text = T, col = heat.colors (7), xlab = 'Sample standardisation',
         ylab = 'Species richness', names.arg = c('sample area', '# of individuals', 'sample coverage'))

```

```{r, fig.height = 6, fig.width = 10}

matplot(scale (D_est), type = 'b', axes = F, xlab = 'Locality', ylab = 'Standardized species richness')
axis(1, at = 1:10, labels = rownames(D_est), las=2)
axis(2)
box()
legend('topright', title = 'Diversity standardised by:', legend = c('sample area', '# individuals', 'sample coverage'), pch = as.character(1:3), col = 1:3, lty = 1:3)

```







