---
title: "Dung_Beetle_Landscape_EDA"
author: "Chloe Cho"
date: "2022-12-09"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(ggplot2)
library(Hmisc)
library(reshape)
library(fitdistrplus)
library(lme4)
library(janitor)
library(ggthemes)
library(ggsignif)
library(broom)
library(rstatix)

```

**Read data** - Landscape data for the ten dung beetle sites.

```{r}

dung_beetle_landscape <- read.delim("../QGIS/Final_CDL_Dung_Beetle_2021.csv", sep = ",")
dung_beetle_landscape

```
Adding a column that combines natural and semi-natural land-use types. 100% would equal agriculture + developed + semi-natural/natural. 

```{r}

dung_beetle_250m <- dung_beetle_landscape %>%
  dplyr::rename(Site = na) %>%
  dplyr::select(Site, AG_250:AG_PAST_250) %>%
  mutate(NAT_SEMINAT_250 = PAST_250 + NAT_FOR_250 + NAT_OPEN_250)

```

```{r}

dung_beetle_500m <- dung_beetle_landscape %>%
  dplyr::rename(Site = na) %>%
  dplyr::select(Site, AG_500:AG_PAST_500) %>%
  mutate(NAT_SEMINAT_500 = PAST_500 + NAT_FOR_500 + NAT_OPEN_500)

```

```{r}

dung_beetle_750m <- dung_beetle_landscape %>%
  dplyr:: rename(Site = na) %>%
  dplyr::select(Site, AG_750:AG_PAST_750) %>%
  mutate(NAT_SEMINAT_750 = PAST_750 + NAT_FOR_750 + NAT_OPEN_750)

```

```{r}

dung_beetle_1000m <- dung_beetle_landscape %>%
  dplyr::rename(Site = na) %>%
  dplyr::select(Site, AG_1000:AG_PAST_1000) %>%
  mutate(NAT_SEMINAT_1000 = PAST_1000 + NAT_FOR_1000 + NAT_OPEN_1000)

```

**Read data** - Dung beetle species count data + other beetle families (Histeridae, Hydrophilidae, Staphylinidae, Scarabaeidae) + face flies + horn flies. Source: Ken Wise.

```{r}

beetle_counts <- read.delim("../Data/Dung_Beetle_Data.csv", sep = ",")
beetle_counts

```

Renaming Farm names to match landscape data variable names so tables can be joined. 

```{r}

beetle_counts$Farm[beetle_counts$Farm == 'Chaseholm'] <- 'Chaseholm_Farm_NI'
beetle_counts$Farm[beetle_counts$Farm == 'Wallbridge'] <- 'Wallbridge_Farm_I'
beetle_counts$Farm[beetle_counts$Farm == 'Johnk Farm'] <- 'Johnk_Farm_NI'
beetle_counts$Farm[beetle_counts$Farm == 'Boone Farm'] <- 'Boone_Farm_I'
beetle_counts$Farm[beetle_counts$Farm == 'Honeyhill'] <- 'Honeyhill_Farm_NI'
beetle_counts$Farm[beetle_counts$Farm == 'Rugenstein Family Farm'] <- 'Rugenstein_Family_Farm_I'
beetle_counts$Farm[beetle_counts$Farm == 'Turner'] <- 'Turner_Farm_NI'
beetle_counts$Farm[beetle_counts$Farm == 'Kuipers'] <- 'Kuipers_Farm_I'
beetle_counts$Farm[beetle_counts$Farm == 'Eisele farm'] <- 'Eisele_Farm_NI'
beetle_counts$Farm[beetle_counts$Farm == 'Shephard farm'] <- 'Shephard_Farm_I'

beetle_counts

```

Reformat Date column into date data type. 

```{r}

date_format <- as.Date(beetle_counts$Date, '%m/%d/%y')

beetle_counts <- beetle_counts %>%
  dplyr::mutate(Date = date_format) %>%
  clean_names() %>%
  dplyr::mutate(non_or_insecticide = tolower(non_or_insecticide)) %>%
  dplyr::mutate(weather = tolower(weather)) %>%
  dplyr::mutate(farm = tolower(farm)) %>%
  dplyr::mutate(active_ingredients = tolower(active_ingredients)) %>%
  dplyr::mutate(region = tolower(region)) %>%
  mutate(non_or_insecticide = case_when(non_or_insecticide == 'non   ' ~ 'non',
                                        non_or_insecticide == 'insecticide' ~ 'insecticide',
                                        non_or_insecticide == 'non' ~ 'non'))

beetle_counts

```

**Dung Beetle EDA**

Plot species over time. Calamosternus granarius and Colobopterus erraticus seem to appear most frequently. This is more apparent in the earlier season.  

Melt table into vertical format so there is one count data point per row. 

```{r}

dung_beetles <- beetle_counts %>%
  dplyr::select(date:onthophagus_hecate)
  
dung_beetles <- melt(dung_beetles, id = c("farm", "region", "date", "temp", "weather", "non_or_insecticide", "active_ingredients")) 

```

Graph beetle counts by species, color coded by farm. *See if there is a way to group together the fifteen species based on their ecological behavior to help simplify visualization.*

```{r}

dung_beetles %>%
  group_by(farm, variable) %>%
  replace(is.na(dung_beetles), 0) %>%
  summarise(total = sum(value)) %>%
  ggplot(aes(variable, total, col = farm)) + 
  geom_point() + 
  scale_x_discrete(guide = guide_axis(angle = 45))

```

```{r}

dung_beetles %>%
  group_by(farm, variable) %>%
  replace(is.na(dung_beetles), 0) %>%
  #summarise(total = sum(value)) %>%
  filter(farm == 'boone_farm_i') %>%
  ggplot(aes(x = variable, y = log(value))) +
  geom_boxplot() +
  scale_x_discrete(guide = guide_axis(angle = 45))

```

Summed dung beetles per farm. *Potential visualization idea is to get a few ecological categories and have multiple bars per farm. Then, these bars could be split into stacks that represent the individual species counts.*

```{r}

dung_beetles %>%
  group_by(farm) %>%
  replace(is.na(dung_beetles), 0) %>%
  summarise(total = sum(value)) %>%
  ggplot(aes(x = farm, y = total)) +
  geom_bar(stat = 'identity') +
  scale_x_discrete(guide = guide_axis(angle = 45))

```

Checking for distribution. Negative binomial fits slightly better - will continue to use a negative binomial distribution for the following models. 

```{r}

cleaned_dung_beetles <- dung_beetles %>%
  replace(is.na(dung_beetles), 0) %>%
  mutate(non_or_insecticide = case_when(non_or_insecticide == 'non   ' ~ 'non',
                                        non_or_insecticide == 'insecticide' ~ 'insecticide',
                                        non_or_insecticide == 'non' ~ 'non')) %>%
  mutate(across(c(weather, non_or_insecticide, active_ingredients, farm, region),
                factor)) 

plot(fitdist(cleaned_dung_beetles$value,"nbinom"))
plot(fitdist(cleaned_dung_beetles$value,"pois"))

```

Graphing insecticide vs. non-insecticide. 

```{r}

non_or_insecticide_counts <- cleaned_dung_beetles %>%
  group_by(non_or_insecticide) %>%
  summarise(freq = sum(value))

group_means <- cleaned_dung_beetles %>%
  group_by(non_or_insecticide) %>%
  summarise(mean = mean(value),
            n = n())

cleaned_dung_beetles %>% ggplot(aes(x = non_or_insecticide, y = value, fill = non_or_insecticide)) +
  geom_boxplot() 

cleaned_dung_beetles %>% t_test(value ~ non_or_insecticide,
                var.equal = TRUE,
                detailed = TRUE) %>%
  glimpse()

cleaned_dung_beetles %>%
  group_by(non_or_insecticide) %>%
  ggplot(aes(x = non_or_insecticide, y = value)) +
  geom_boxplot() +
  geom_signif(comparisons = list(c("insecticide", "non")),
              test = "t.test", 
              map_signif_level = TRUE)
```

Running an initial model with just the random effects.

```{r}

initial_model <- glmer.nb(value ~ (1 | region/farm), data = cleaned_dung_beetles)
summary(initial_model)

```

Adding a fixed effect to the model - insecticide/non-insecticide. Region and farm are random effects. 

No significance found. 

```{r}

model_1 <- glmer.nb(value ~ non_or_insecticide + (1 | region/farm), data = cleaned_dung_beetles)
summary(model_1)

```

Merge local and landscape data. 

```{r}

dung_beetle_landscape <- dung_beetle_landscape %>% 
  clean_names() %>%
  dplyr::rename(farm = na) %>%
  mutate(farm = tolower(farm)) %>%
  mutate(farm = factor(farm))

```

```{r}

cleaned_dung_beetles

```

Join the local and landscape data frames. 

```{r}

local_landscape_joined <- cleaned_dung_beetles %>%
  left_join(dung_beetle_landscape, by = c("farm" = "farm"))

```

**Dung Beetles - Looking at 250m buffer**

```{r}

dung_beetle_250m <- dung_beetle_250m %>% 
  clean_names() %>%
  dplyr::rename(farm = site) %>%
  dplyr::mutate(farm = tolower(farm))
  
local_landscape_250m <- cleaned_dung_beetles %>%
  left_join(dung_beetle_250m, by = c("farm" = "farm"))

```

```{r}

ggplot(local_landscape_250m, aes(x = nat_seminat_250, y = log(value), color = non_or_insecticide)) + 
  geom_point() + 
  theme_few() + 
  ylab('Dung Beetle (log)') +
  xlab('Proportion Natural/Semi-Natural 250m') + 
  geom_smooth(method = lm)

```

For all dung beetle species combined at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance for temperature, local (insecticide use), and local*landscape interaction. 

```{r}

model_250 <- glmer.nb(value ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = local_landscape_250m)
summary(model_250)

```

**Dung Beetles - Looking at 500m buffer**

```{r}

dung_beetle_500m <- dung_beetle_500m %>% 
  clean_names() %>%
  dplyr::rename(farm = site) %>%
  dplyr::mutate(farm = tolower(farm))
  
local_landscape_500m <- cleaned_dung_beetles %>%
  left_join(dung_beetle_500m, by = c("farm" = "farm"))

```

```{r}

ggplot(local_landscape_500m, aes(x = nat_seminat_500, y = log(value), color = non_or_insecticide)) + 
  geom_point() + 
  theme_few() + 
  ylab('Dung Beetle (log)') +
  xlab('Proportion Natural/Semi-Natural 500m') + 
  geom_smooth(method = lm)

```

For all dung beetle species combined at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Significance for temperature. Marginal significance for insecticide/non-insecticide and local*landscape interaction. 

```{r}

model_500 <- glmer.nb(value ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = local_landscape_500m)
summary(model_500)

```

**Dung Beetles - Looking at 750m buffer**

```{r}

dung_beetle_750m <- dung_beetle_750m %>% 
  clean_names() %>%
  dplyr::rename(farm = site) %>%
  dplyr::mutate(farm = tolower(farm))
  
local_landscape_750m <- cleaned_dung_beetles %>%
  left_join(dung_beetle_750m, by = c("farm" = "farm"))

```

```{r}

ggplot(local_landscape_750m, aes(x = nat_seminat_750, y = log(value), color = non_or_insecticide)) + 
  geom_point() + 
  theme_few() + 
  ylab('Dung Beetle (log)') +
  xlab('Proportion Natural/Semi-Natural 750m') +  
  geom_smooth(method = lm)

```

For all dung beetle species combined at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Significance for temperature and landscape. Marginal significance for insecticide/non-insecticide. 

```{r}

model_750 <- glmer.nb(value ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = local_landscape_750m)

summary(model_750)

```

**Dung Beetles - Looking at 1000m buffer**

```{r}

dung_beetle_1000m <- dung_beetle_1000m %>% 
  clean_names() %>%
  dplyr::rename(farm = site) %>%
  dplyr::mutate(farm = tolower(farm))
  
local_landscape_1000m <- cleaned_dung_beetles %>%
  left_join(dung_beetle_1000m, by = c("farm" = "farm"))

```

```{r}

ggplot(local_landscape_1000m, aes(x = nat_seminat_1000, y = log(value), color = non_or_insecticide)) + 
  geom_point() + 
  theme_few() + 
  ylab('Dung Beetle (log)') +
  xlab('Proportion Natural/Semi-Natural 1000m') +
  geom_smooth(method = lm)

```

For all dung beetle species combined at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Significance for temperature, non-insecticide/insecticide, and landscape. 

```{r}

model_1000 <- glmer.nb(value ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = local_landscape_1000m)

summary(model_1000)

```

**Other Beetle Families - 250m**

Modeling the other three beetle families collected and identified in relationship to local and landscape factors. 

```{r}
beetle_counts <- beetle_counts %>%
  mutate(across(c(weather, non_or_insecticide, active_ingredients, farm, region),
                factor)) 


families_250 <- beetle_counts %>%
  dplyr::select(date:active_ingredients, histeridae:scarabaeidae) %>%
  replace(is.na(.), 0) %>%
  left_join(dung_beetle_250m, by = c("farm" = "farm"))

```

For family Histeridae at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance for temperature, insecticide/non-insecticide, and the local*landscape interaction. Marginal significance for the landscape factor. 

```{r}

plot(fitdist(families_250$histeridae,"nbinom"))
plot(fitdist(families_250$histeridae,"pois"))

histeridae_250 <- glmer.nb(histeridae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = families_250)
summary(histeridae_250)

```

For family Hydrophilidae at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance for temperature. 

```{r}

plot(fitdist(families_250$hydrophilidae,"nbinom"))
plot(fitdist(families_250$hydrophilidae,"pois"))

hydrophilidae_250 <- glmer.nb(hydrophilidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = families_250)
summary(hydrophilidae_250)

```

For family Staphylinidae at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance for insecticide/non-insecticide, and the local*landscape interaction. Marginal significance for the landscape factor. 

```{r}

plot(fitdist(families_250$staphylinidae,"nbinom"))
plot(fitdist(families_250$staphylinidae,"pois"))

staphylinidae_250 <- glmer.nb(staphylinidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = families_250)
summary(staphylinidae_250)

```

**Other Beetle Families - 500m**

```{r}

families_500 <- beetle_counts %>%
  dplyr::select(date:active_ingredients, histeridae:scarabaeidae) %>%
  replace(is.na(.), 0) %>%
  left_join(dung_beetle_500m, by = c("farm" = "farm"))

```

For family Histeridae at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Model failed to converge. Need to try other optimizers. 

```{r}

histeridae_500 <- glmer.nb(histeridae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = families_500)
summary(histeridae_500)

```

For family Hydrophilidae at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Model did not converge.

```{r}

hydrophilidae_500 <- glmer.nb(hydrophilidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = families_500)
summary(hydrophilidae_500)

```

For family Staphylinidae at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Significance for landscape. 

```{r}

staphylinidae_500 <- glmer.nb(staphylinidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = families_500)
summary(staphylinidae_500)

```

**Other Beetle Families - 750m**

```{r}

families_750 <- beetle_counts %>%
  dplyr::select(date:active_ingredients, histeridae:scarabaeidae) %>%
  replace(is.na(.), 0) %>%
  left_join(dung_beetle_750m, by = c("farm" = "farm"))

```

For family Histeridae at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Model failed to converge. Need to try other optimizers. 

```{r}

histeridae_750 <- glmer.nb(histeridae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = families_750)
summary(histeridae_750)

```

For family Hydrophilidae at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Significance for insecticide/non-insecticide and local*landscape. Marginal significance for temperature. 

```{r}

hydrophilidae_750 <- glmer.nb(hydrophilidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = families_750)
summary(hydrophilidae_750)

```

For family Staphylinidae at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Model failed to converge. Need to try other optimizers. 

```{r}

staphylinidae_750 <- glmer.nb(staphylinidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = families_750)
summary(staphylinidae_750)

```

**Other Beetle Families - 1000m**

```{r}

families_1000 <- beetle_counts %>%
  dplyr::select(date:active_ingredients, histeridae:scarabaeidae) %>%
  replace(is.na(.), 0) %>%
  left_join(dung_beetle_1000m, by = c("farm" = "farm"))

```

For family Histeridae at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Significance found for temperature. Marginal significance for landscape. 

```{r}

histeridae_1000 <- glmer.nb(histeridae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = families_1000)
summary(histeridae_1000)

```

For family Hydrophilidae at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Marginal significance for temperature, insecticide/non-insecticide, landscape, and local*landscape interaction. 

```{r}

hydrophilidae_1000 <- glmer.nb(hydrophilidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = families_1000)
summary(hydrophilidae_1000)

```

For family Staphylinidae at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Significance found for landscape. 

```{r}

staphylinidae_1000 <- glmer.nb(staphylinidae ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = families_1000)
summary(staphylinidae_1000)

```

**Fly Abundance**

```{r}

flies <- beetle_counts %>%
  dplyr::select(date:active_ingredients, horn_flies:face_flies) %>%
  mutate(horn_flies = as.integer(horn_flies)) 

flies[is.na(flies)] <- 0

```

**Flies - 250m Buffer**

For horn flies at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance found for temperature. Marginal significance for insecticide/non-insecticide, local*landscape interaction. 

```{r}

plot(fitdist(flies$horn_flies,"nbinom"))
plot(fitdist(flies$horn_flies,"pois"))

flies_landscape_250 <- flies %>%
  left_join(dung_beetle_250m, by = c("farm" = "farm"))
  
horn_flies_250m <- glmer.nb(horn_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = flies_landscape_250)
summary(horn_flies_250m)

```

For face flies at 250m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 250m radius. Random effects are region and farm. 

Significance found for temperature.  

```{r}

face_flies_250m <- glmer.nb(face_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_250) + (1 | region/farm), data = flies_landscape_250)
summary(face_flies_250m)

```

**Flies - 500m Buffer**

For horn flies at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Significance found for temperature.

```{r}

flies_landscape_500 <- flies %>%
  left_join(dung_beetle_500m, by = c("farm" = "farm"))
  
horn_flies_500m <- glmer.nb(horn_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = flies_landscape_500)
summary(horn_flies_500m)

```

For face flies at 500m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 500m radius. Random effects are region and farm. 

Model did not converge. 

```{r}

face_flies_500m <- glmer.nb(face_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_500) + (1 | region/farm), data = flies_landscape_500)
summary(face_flies_500m)

```

**Flies - 750m Buffer**

For horn flies at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Significance found for temperature.

```{r}

flies_landscape_750 <- flies %>%
  left_join(dung_beetle_750m, by = c("farm" = "farm"))
  
horn_flies_750m <- glmer.nb(horn_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = flies_landscape_750)
summary(horn_flies_750m)

```

For face flies at 750m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 750m radius. Random effects are region and farm. 

Model did not converge. 

```{r}

face_flies_750m <- glmer.nb(face_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_750) + (1 | region/farm), data = flies_landscape_750)
summary(face_flies_750m)

```

**Flies - 1000m Buffer**

For horn flies at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Significance found for temperature. Marginal significance for landscape. 

```{r}

flies_landscape_1000 <- flies %>%
  left_join(dung_beetle_1000m, by = c("farm" = "farm"))
  
horn_flies_1000m <- glmer.nb(horn_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = flies_landscape_1000)
summary(horn_flies_1000m)

```

For face flies at 1000m - explanatory variables are temperature, insecticide use, and combined proportion of semi-natural and natural habitat at 1000m radius. Random effects are region and farm. 

Model did not converge. 

```{r}

face_flies_1000m <- glmer.nb(face_flies ~ scale(temp) + non_or_insecticide * scale(nat_seminat_1000) + (1 | region/farm), data = flies_landscape_1000)
summary(face_flies_1000m)

```





