---
title: "SWD CDL Processing"
author: "Chloe Cho"
date: "2022-12-07"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(dplyr)
library(janitor)
```

NEW YORK

Data upload--the QGIS output at 4 different scales and the 2021 New York CDL Metadata.

```{r}

CDL_Metadata_NY <- read.delim("CDL_Metadata_2021_NY.csv", sep = ",")
CDL_150_NY <- read.delim("QGIS/swd_ny_sites/swd_ny_150m.csv", sep = ",")
CDL_250_NY <- read.delim("QGIS/swd_ny_sites/swd_ny_250m.csv", sep = ",")
CDL_500_NY <- read.delim("QGIS/swd_ny_sites/swd_ny_500m.csv", sep = ",")
CDL_1000_NY <- read.delim("QGIS/swd_ny_sites/swd_ny_1000m.csv", sep = ",")
```

Formatting the metadata so that it can be merged with the QGIS output files--the CDL number needs to have "Value" written in front of it so that it can match.

```{r}

CDL_Metadata_NY <- CDL_Metadata_NY %>% 
  mutate(cdl_code = paste("Value", cdl_number, sep = "_"))

```

Merging QGIS outputs with the metadata so that the crops are displayed by name not value.

```{r}

CDL_150_w_crops_NY <- CDL_150_NY %>% 
  select(Name, Value_1:Value_243) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_250_w_crops_NY <- CDL_250_NY %>% 
  select(Name, Value_1:Value_243) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_500_w_crops_NY <- CDL_500_NY %>% 
  select(Name, Value_1:Value_243) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])

CDL_1000_w_crops_NY <- CDL_1000_NY %>% 
  select(Name, Value_1:Value_243) %>% 
  setNames(CDL_Metadata_NY$cdl_classification[match(names(.), CDL_Metadata_NY$cdl_code)])


```

Grouping crops to create broad landscape categories - 150m.

```{r}

CDL_150_Summary_NY <- CDL_150_w_crops_NY %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_150 = ((corn + soybeans + winter_wheat + rye + oats + speltz + alfalfa + grapes + blueberries + cabbage + dry_beans + fallow_idle_cropland) / Total),
         PAST_150 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_150 = ((deciduous_forest + mixed_forest + woody_wetlands) / Total), 
        # NAT_OPEN_150 = ((clover_wildflowers+shrubland+herbaceous_wetlands+developed_open_space)/Total),
        # DEV_150 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren)/Total),
         NAT_150 = NAT_FOR_150, # + NAT_OPEN_150
         NAT_PAST_150 = PAST_150, # + NAT_OPEN_150
         AG_PAST_150 = AG_150 + PAST_150
        ) %>% 
    select(na, AG_150:AG_PAST_150)

```

Grouping crops to create broad landscape categories - 250m.

```{r}

CDL_250_Summary_NY <- CDL_250_w_crops_NY %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_250 = ((corn + soybeans + winter_wheat + rye + oats + speltz + alfalfa + grapes + blueberries + cabbage + dry_beans + fallow_idle_cropland) / Total),
         PAST_250 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_250 = ((deciduous_forest + mixed_forest + woody_wetlands) / Total), 
        # NAT_OPEN_150 = ((clover_wildflowers+shrubland+herbaceous_wetlands+developed_open_space)/Total),
        # DEV_150 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren)/Total),
         NAT_250 = NAT_FOR_250, # + NAT_OPEN_150
         NAT_PAST_250 = PAST_250, # + NAT_OPEN_150
         AG_PAST_250 = AG_250 + PAST_250
        ) %>% 
    select(na, AG_250:AG_PAST_250)

```

Grouping crops to create broad landscape categories - 500m.

```{r}

CDL_500_Summary_NY <- CDL_500_w_crops_NY %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_500 = ((corn + soybeans + winter_wheat + rye + oats + speltz + alfalfa + grapes + blueberries + cabbage + dry_beans + fallow_idle_cropland) / Total),
         PAST_500 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_500 = ((deciduous_forest + mixed_forest + woody_wetlands) / Total), 
        # NAT_OPEN_150 = ((clover_wildflowers+shrubland+herbaceous_wetlands+developed_open_space)/Total),
        # DEV_150 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren)/Total),
         NAT_500 = NAT_FOR_500, # + NAT_OPEN_150
         NAT_PAST_500 = PAST_500, # + NAT_OPEN_150
         AG_PAST_500 = AG_500 + PAST_500
        ) %>% 
    select(na, AG_500:AG_PAST_500)

```

Grouping crops to create broad landscape categories - 1000m.

```{r}

CDL_1000_Summary_NY <- CDL_1000_w_crops_NY %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
        AG_1000 = ((corn + soybeans + winter_wheat + rye + oats + speltz + alfalfa + grapes + blueberries + cabbage + dry_beans + fallow_idle_cropland) / Total),
         PAST_1000 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_1000 = ((deciduous_forest + mixed_forest + woody_wetlands) / Total), 
        # NAT_OPEN_150 = ((clover_wildflowers+shrubland+herbaceous_wetlands+developed_open_space)/Total),
        # DEV_150 = ((developed_low_intensity + developed_med_intensity + developed_high_intensity + barren)/Total),
         NAT_1000 = NAT_FOR_1000, # + NAT_OPEN_150
         NAT_PAST_1000 = PAST_1000, # + NAT_OPEN_150
         AG_PAST_1000 = AG_1000 + PAST_1000
        ) %>% 
    select(na, AG_1000:AG_PAST_1000)

```

Joining the four different scales.

```{r}

Final_CDL_SWD_2021_NY <- CDL_150_Summary_NY %>% 
  left_join(CDL_250_Summary_NY) %>% 
  left_join(CDL_500_Summary_NY) %>% 
  left_join(CDL_1000_Summary_NY) # %>% 
  # rename(Site = na) %>% 
  #filter(Site %in% c("Indian_Creek_B1", "CU_Orchards_B", "Stick_and_Stone_B", "West_Haven_B", "Grisamore_B", "Silver_Queen_B", "Shared_Roots_B2", "Cassim_B","Buried_Treasures_B", "Research_North_B2","Fellenz_B","Full_Circle_B","Sampson_B", "Remembrance_B")) %>% 
  #mutate(Site = recode(Site, "Indian_Creek_B1" = "IC", "CU_Orchards_B" = "CO", "Stick_and_Stone_B" = "SS", "West_Haven_B" = "WH", "Grisamore_B" = "GR", "Silver_Queen_B" = "SQ", "Shared_Roots_B2" = "SR", "Cassim_B" = "CA", "Buried_Treasures_B" = "BT", "Research_North_B2" = "RN", "Fellenz_B" = "FE", "Full_Circle_B" = "FC", "Sampson_B" = "SA", "Remembrance_B" = "RE"))
  
```
Writing the csv file for the 2021 CDL data.

```{r}

#write.csv(Final_CDL_SWD_2021_NY, file = "QGIS/swd_ny_sites/Final_CDL_SWD_2021_NY.csv")

```

MAINE

Data upload--the QGIS output at 4 different scales and the 2021 Maine CDL Metadata.

```{r}

CDL_Metadata_ME <- read.delim("CDL_Metadata_2021_ME.csv", sep = ",")
CDL_150_ME <- read.delim("QGIS/swd_me_sites/swd_me_150m.csv", sep = ",")
CDL_250_ME <- read.delim("QGIS/swd_me_sites/swd_me_250m.csv", sep = ",")
CDL_500_ME <- read.delim("QGIS/swd_me_sites/swd_me_500m.csv", sep = ",")
CDL_1000_ME <- read.delim("QGIS/swd_me_sites/swd_me_1000m.csv", sep = ",")
```

Formatting the metadata so that it can be merged with the QGIS output files--the CDL number needs to have "Value" written in front of it so that it can match.

```{r}

CDL_Metadata_ME <- CDL_Metadata_ME %>% 
  mutate(cdl_code = paste("Value", cdl_number, sep = "_"))

```

Merging QGIS outputs with the metadata so that the crops are displayed by name not value.

```{r}

CDL_150_w_crops_ME <- CDL_150_ME %>% 
  select(Name, Value_37:Value_242) %>% 
  setNames(CDL_Metadata_ME$cdl_classification[match(names(.), CDL_Metadata_ME$cdl_code)])

CDL_250_w_crops_ME <- CDL_250_ME %>% 
  select(Name, Value_37:Value_242) %>% 
  setNames(CDL_Metadata_ME$cdl_classification[match(names(.), CDL_Metadata_ME$cdl_code)])

CDL_500_w_crops_ME <- CDL_500_ME %>% 
  select(Name, Value_37:Value_242) %>% 
  setNames(CDL_Metadata_ME$cdl_classification[match(names(.), CDL_Metadata_ME$cdl_code)])

CDL_1000_w_crops_ME <- CDL_1000_ME %>% 
  select(Name, Value_37:Value_242) %>% 
  setNames(CDL_Metadata_ME$cdl_classification[match(names(.), CDL_Metadata_ME$cdl_code)])


```

Grouping crops to create broad landscape categories - 150m.

```{r}

CDL_150_Summary_ME <- CDL_150_w_crops_ME %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_150 = ((blueberries) / Total),
         PAST_150 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_150 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_150 = ((developed_open_space + shrubland + herbaceous_wetlands)/Total),
         DEV_150 = ((developed_low_intensity)/Total),
         NAT_150 = NAT_FOR_150 + NAT_OPEN_150,
         NAT_PAST_150 = PAST_150 + NAT_OPEN_150, 
         AG_PAST_150 = AG_150 + PAST_150
        ) %>% 
    select(na, AG_150:AG_PAST_150)

```

Grouping crops to create broad landscape categories - 250m.

```{r}

CDL_250_Summary_ME <- CDL_250_w_crops_ME %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_250 = ((blueberries) / Total),
         PAST_250 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_250 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_250 = ((developed_open_space + shrubland + herbaceous_wetlands) / Total),
         DEV_250 = ((developed_low_intensity) / Total),
         NAT_250 = NAT_FOR_250 + NAT_OPEN_250,
         NAT_PAST_250 = PAST_250 + NAT_OPEN_250, 
         AG_PAST_250 = AG_250 + PAST_250
        ) %>% 
    select(na, AG_250:AG_PAST_250)

```

Grouping crops to create broad landscape categories - 500m.

```{r}

CDL_500_Summary_ME <- CDL_500_w_crops_ME %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_500 = ((blueberries) / Total),
         PAST_500 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_500 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_500 = ((developed_open_space + shrubland + herbaceous_wetlands) / Total),
         DEV_500 = ((developed_low_intensity) / Total),
         NAT_500 = NAT_FOR_500 + NAT_OPEN_500,
         NAT_PAST_500 = PAST_500 + NAT_OPEN_500, 
         AG_PAST_500 = AG_500 + PAST_500
        ) %>% 
    select(na, AG_500:AG_PAST_500)

```

Grouping crops to create broad landscape categories - 1000m.

```{r}

CDL_1000_Summary_ME <- CDL_1000_w_crops_ME %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_1000 = ((blueberries) / Total),
         PAST_1000 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_1000 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_1000 = ((developed_open_space + shrubland + herbaceous_wetlands) / Total),
         DEV_1000 = ((developed_low_intensity) / Total),
         NAT_1000 = NAT_FOR_1000 + NAT_OPEN_1000,
         NAT_PAST_1000 = PAST_1000 + NAT_OPEN_1000, 
         AG_PAST_1000 = AG_1000 + PAST_1000
        ) %>% 
    select(na, AG_1000:AG_PAST_1000)

```

Joining the four different scales.

```{r}

Final_CDL_SWD_2021_ME <- CDL_150_Summary_ME %>% 
  left_join(CDL_250_Summary_ME) %>% 
  left_join(CDL_500_Summary_ME) %>% 
  left_join(CDL_1000_Summary_ME) # %>% 
  # rename(Site = na) %>% 
  #filter(Site %in% c("Indian_Creek_B1", "CU_Orchards_B", "Stick_and_Stone_B", "West_Haven_B", "Grisamore_B", "Silver_Queen_B", "Shared_Roots_B2", "Cassim_B","Buried_Treasures_B", "Research_North_B2","Fellenz_B","Full_Circle_B","Sampson_B", "Remembrance_B")) %>% 
  #mutate(Site = recode(Site, "Indian_Creek_B1" = "IC", "CU_Orchards_B" = "CO", "Stick_and_Stone_B" = "SS", "West_Haven_B" = "WH", "Grisamore_B" = "GR", "Silver_Queen_B" = "SQ", "Shared_Roots_B2" = "SR", "Cassim_B" = "CA", "Buried_Treasures_B" = "BT", "Research_North_B2" = "RN", "Fellenz_B" = "FE", "Full_Circle_B" = "FC", "Sampson_B" = "SA", "Remembrance_B" = "RE"))
  
```
Writing the csv file for the 2021 CDL data.

```{r}

#write.csv(Final_CDL_SWD_2021_ME, file = "QGIS/swd_me_sites/Final_CDL_SWD_2021_ME.csv")

```

NEW JERSEY

Data upload--the QGIS output at 4 different scales and the 2021 New Jersey CDL Metadata.

```{r}

CDL_Metadata_NJ <- read.delim("CDL_Metadata_2021_NJ.csv", sep = ",")
CDL_150_NJ <- read.delim("QGIS/swd_nj_sites/swd_nj_150m.csv", sep = ",")
CDL_250_NJ <- read.delim("QGIS/swd_nj_sites/swd_nj_250m.csv", sep = ",")
CDL_500_NJ <- read.delim("QGIS/swd_nj_sites/swd_nj_500m.csv", sep = ",")
CDL_1000_NJ <- read.delim("QGIS/swd_nj_sites/swd_nj_1000m.csv", sep = ",")
```

Formatting the metadata so that it can be merged with the QGIS output files--the CDL number needs to have "Value" written in front of it so that it can match.

```{r}

CDL_Metadata_NJ <- CDL_Metadata_NJ %>% 
  mutate(cdl_code = paste("Value", cdl_number, sep = "_"))

```

Merging QGIS outputs with the metadata so that the crops are displayed by name not value.

```{r}

CDL_150_w_crops_NJ <- CDL_150_NJ %>% 
  select(Name, Value_1:Value_242) %>% 
  setNames(CDL_Metadata_NJ$cdl_classification[match(names(.), CDL_Metadata_NJ$cdl_code)])

CDL_250_w_crops_NJ <- CDL_250_NJ %>% 
  select(Name, Value_1:Value_242) %>% 
  setNames(CDL_Metadata_NJ$cdl_classification[match(names(.), CDL_Metadata_NJ$cdl_code)])

CDL_500_w_crops_NJ <- CDL_500_NJ %>% 
  select(Name, Value_1:Value_242) %>% 
  setNames(CDL_Metadata_NJ$cdl_classification[match(names(.), CDL_Metadata_NJ$cdl_code)])

CDL_1000_w_crops_NJ <- CDL_1000_NJ %>% 
  select(Name, Value_1:Value_242) %>% 
  setNames(CDL_Metadata_NJ$cdl_classification[match(names(.), CDL_Metadata_NJ$cdl_code)])


```

Grouping crops to create broad landscape categories - 150m.

```{r}

CDL_150_Summary_NJ <- CDL_150_w_crops_NJ %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_150 = ((corn + soybeans + blueberries) / Total),
         PAST_150 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_150 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_150 = ((developed_open_space + shrubland + herbaceous_wetlands)/Total),
         DEV_150 = ((developed_low_intensity + developed_med_intensity + barren)/Total),
         NAT_150 = NAT_FOR_150 + NAT_OPEN_150,
         NAT_PAST_150 = PAST_150 + NAT_OPEN_150, 
         AG_PAST_150 = AG_150 + PAST_150
        ) %>% 
    select(na, AG_150:AG_PAST_150)

```

Grouping crops to create broad landscape categories - 250m.

```{r}

CDL_250_Summary_NJ <- CDL_250_w_crops_NJ %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_250 = ((corn + soybeans + blueberries) / Total),
         PAST_250 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_250 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_250 = ((developed_open_space + shrubland + herbaceous_wetlands)/Total),
         DEV_250 = ((developed_low_intensity + developed_med_intensity + barren)/Total),
         NAT_250 = NAT_FOR_250 + NAT_OPEN_250,
         NAT_PAST_250 = PAST_250 + NAT_OPEN_250, 
         AG_PAST_250 = AG_250 + PAST_250
        ) %>% 
    select(na, AG_250:AG_PAST_250)

```

Grouping crops to create broad landscape categories - 500m.

```{r}

CDL_500_Summary_NJ <- CDL_500_w_crops_NJ %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_500 = ((corn + soybeans + blueberries) / Total),
         PAST_500 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_500 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_500 = ((developed_open_space + shrubland + herbaceous_wetlands)/Total),
         DEV_500 = ((developed_low_intensity + developed_med_intensity + barren)/Total),
         NAT_500 = NAT_FOR_500 + NAT_OPEN_500,
         NAT_PAST_500 = PAST_500 + NAT_OPEN_500, 
         AG_PAST_500 = AG_500 + PAST_500
        ) %>% 
    select(na, AG_500:AG_PAST_500)

```

Grouping crops to create broad landscape categories - 1000m.

```{r}

CDL_1000_Summary_NJ <- CDL_1000_w_crops_NJ %>% 
  clean_names() %>% 
   mutate(Total = rowSums(across(where(is.numeric))),
         AG_1000 = ((corn + soybeans + blueberries) / Total),
         PAST_1000 = ((other_hay_non_alfalfa + grassland_pasture) / Total),
         NAT_FOR_1000 = ((deciduous_forest + evergreen_forest + mixed_forest + woody_wetlands) / Total), 
         NAT_OPEN_1000 = ((developed_open_space + shrubland + herbaceous_wetlands)/Total),
         DEV_1000 = ((developed_low_intensity + developed_med_intensity + barren)/Total),
         NAT_1000 = NAT_FOR_1000 + NAT_OPEN_1000,
         NAT_PAST_1000 = PAST_1000 + NAT_OPEN_1000, 
         AG_PAST_1000 = AG_1000 + PAST_1000
        ) %>% 
    select(na, AG_1000:AG_PAST_1000)

```

Joining the four different scales.

```{r}

Final_CDL_SWD_2021_NJ <- CDL_150_Summary_NJ %>% 
  left_join(CDL_250_Summary_NJ) %>% 
  left_join(CDL_500_Summary_NJ) %>% 
  left_join(CDL_1000_Summary_NJ) # %>% 
  # rename(Site = na) %>% 
  #filter(Site %in% c("Indian_Creek_B1", "CU_Orchards_B", "Stick_and_Stone_B", "West_Haven_B", "Grisamore_B", "Silver_Queen_B", "Shared_Roots_B2", "Cassim_B","Buried_Treasures_B", "Research_North_B2","Fellenz_B","Full_Circle_B","Sampson_B", "Remembrance_B")) %>% 
  #mutate(Site = recode(Site, "Indian_Creek_B1" = "IC", "CU_Orchards_B" = "CO", "Stick_and_Stone_B" = "SS", "West_Haven_B" = "WH", "Grisamore_B" = "GR", "Silver_Queen_B" = "SQ", "Shared_Roots_B2" = "SR", "Cassim_B" = "CA", "Buried_Treasures_B" = "BT", "Research_North_B2" = "RN", "Fellenz_B" = "FE", "Full_Circle_B" = "FC", "Sampson_B" = "SA", "Remembrance_B" = "RE"))
  
```
Writing the csv file for the 2021 CDL data.

```{r}

#write.csv(Final_CDL_SWD_2021_NJ, file = "QGIS/swd_nj_sites/Final_CDL_SWD_2021_NJ.csv")

```